% ----------------------------------------------------------------------
% Title:    aTableau.  Author:   Andrew Mathas Created:  October 2023
% Modified: 11:05 Wednesday, 08 January 2025
% ----------------------------------------------------------------------
\documentclass{amsart}
\usepackage[svgnames,table]{xcolor}
\usepackage{atableau}
\usepackage{xspace}
\usepackage{manfnt}
\usepackage{booktabs}
\usepackage{xltabular}
\usepackage{siunitx}
\usepackage{array}
\newcolumntype{L}{>{\sffamily\color{MidnightBlue}\textbackslash}l}

\usepackage{todonotes}
\newcommand\Todo[1]{\todo[color=Red!20!White,inline]{To do: #1}}

% ----------------------------------------------------------------------
\usepackage{bm}
\usepackage{mathtools}

% ----------------------------------------------------------------------
\usepackage{bbding}
\newcommand\Yes{\textcolor{ForestGreen}{\CheckmarkBold}}
\newcommand\No{\textcolor{red}{\XSolidBrush}}

% ----------------------------------------------------------------------
\usepackage[a4paper,hmargin=24mm, vmargin=18mm, footskip=10mm]{geometry}
\synctex=1
\hfuzz=5pt
\parindent=0pt
\parskip=4mm

\makeatletter
\def\@evenhead{\hfill\aTableau\hfill}
\let\@oddhead\@evenhead
\def\@oddfoot {\color{aTableauInner} Version \atableau@version~(\atableau@release)\hfill\thepage}
\def\@evenfoot{\color{aTableauInner} \thepage\hfill Version \atableau@version~(\atableau@release)}
\makeatother

% ----------------------------------------------------------------------
\newcommand\aTableauColour[1]{%
  \tikz[baseline={(current bounding box.south)}]\node[minimum width=8mm, minimum height=2ex,fill=aTableau#1]{};%
}

\usepackage{enumitem}
\setlist{itemsep=2mm, parsep=2mm}
\newlist{options}{description}{1}
\setlist[options]{
    font=\sffamily\bfseries\color{aTableauInner},
    labelwidth=\textwidth
}

\ExplSyntaxOn
% Add hyperinks for (new displayed) options
\prop_new:N \l__atableau_options_prop
\NewDocumentCommand\AddOptionLink{m}
{
   \tl_set:Nx \l_tmpc_tl {Option:\str_lowercase:f{#1}}
   \prop_if_in:NVF \l__atableau_options_prop \l_tmpc_tl
   {
      \phantomsection\label{Option:\str_lowercase:n{#1}}% add a label for references
      \prop_put:NVn \l__atableau_options_prop \l_tmpc_tl {}
   }
}
% \option*[default value]{option name}[accepts]
% The *-version does not do a \bigskip before the option. A hyperlink is
% added for new displayed options. If #2 is blank then the *-version
% puts (no) before the option key.
\NewDocumentCommand\option{ somo }
{%
  \IfNoValueTF{#2}
  {%
    \seq_set_split:Nnn \l_tmpa_seq {=} {#3}%
    \seq_pop_left:NN \l_tmpa_seq \l_tmpa_tl%
    \tl_set:Nn \l_tmpb_tl {Option:\str_lowercase:f{\l_tmpa_tl}}
    \hyperref[\l_tmpb_tl]{\textsf{\color{aTableauInner}\IfBooleanT{#1}{(no)~}\l_tmpa_tl}}%
    \index{\l_tmpa_tl}%
    \seq_if_empty:NF \l_tmpa_seq%
    {
      \textsf{=}%
      \textsf{\color{orange}\seq_use:Nn \l_tmpa_seq {~}}%
    }%
  }
  {%
    \IfBooleanTF{#1}{\newline}{\bigskip}%
    \AddOptionLink{#3}% add a label for references
    \noindent\textsf{\textcolor{aTableauInner}{#3}}%
    \tl_if_blank:nF {#2}{~(default:~\textcolor{DarkRed}{#2})}%
    \hfill%
    \IfNoValueF{#4}{\textcolor{Grey}{[accepts:~#4]}}%
    \index{#3}%
  }%
}

% index command ignoring the backslash and capitalisation
\cs_new_protected:Npn \l_addto_index:nn #1#2 { \index{#2@\textbackslash #1} }
\cs_generate_variant:Nn \l_addto_index:nn {Vo}
\NewDocumentCommand\indexcmd{m}
{
    \tl_set:Nn \l_index_tl  {#1}
    \l_addto_index:Vo \l_index_tl { \str_lower_case:n\l_index_tl }
}
\ExplSyntaxOff

% ---------------------------------------------------------------------------
% the index

\usepackage{imakeidx}
\indexsetup{level=\section*, toclevel=section, noclearpage}
\makeindex[columns=3]
\renewcommand*{\seename}{see}

% ---------------------------------------------------------------------------
%\renewcommand\thesubsection{\thesection\Alph{subsection}}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\renewcommand\thesubsection{\thesection\Alph{subsection}}
\renewcommand\thesubsubsection{\thesubsection.\arabic{subsubsection}}

\makeatletter
\def\l@subsection{\@tocline{2}{0pt}{2.5pc}{5pc}{}}
\def\l@subsubsection{\@tocline{2}{0pt}{3.5pc}{3pc}{}}
\makeatother

\newenvironment{danger}{\trivlist\item[\hskip\labelsep\textcolor{red}{\textdbend}]}{\endtrivlist}

% ---------------------------------------------------------------------------
\usepackage[skins]{tcolorbox}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=MediumBlue,
  citecolor=FireBrick,
}
\tcbuselibrary{listings, breakable}

\DeclareTotalTCBox\keyword{ O{} v }
{
  bottom=0pt,
  colback  = Ivory,
  colupper = aTableauInner,
  fontupper= \bfseries,
  fontlower= \bfseries,
  left     = 0mm,
  right    = 0mm,
  size     = tight,
  skin     = tile,
  top      = 0pt,
  nobeforeafter,
  on line,
  shrink tight,
  verbatim,
  #1}
{#2}

\newcommand\aTableau{\textcolor{aTableauMain}{\sffamily aTableau}\xspace}

% hyperref links to ctan
\newcommand\ctan[1]{\href{https://www.ctan.org/pkg/#1}{\texttt{#1}}}
\newcommand\TikZ{\href{https://www.ctan.org/pkg/tikz}{Ti\textit{k}Z}\xspace}

\lstdefinestyle{atableau}{style=tcblatex,
  classoffset=0,
  texcsstyle=*\color{MediumBlue},%
  deletetexcs={begin, end},
  commentstyle=\color{Peru},
  moretexcs={,% aTableau package commands
    aTabset,
    Abacus,
    Diagram,
    Multidiagram,
    Multitableau,
    RibbonTableau,
    ShiftedDiagram,
    ShiftedTableau,
    SkewTableau,
    SkewDiagram,
    Tableau,
    Tabloid,
  },%
  classoffset=1, % aTableau package options
  keywordstyle=\color{aTableauInner},%
  morekeywords={
    Australian,
    English,
    French,
    Ukrainian,
    align,
    australian,
    border,
    box,
    boxes,
    color,
    colour,
    cols,
    conjugate,
    delimiter,
    delimiters,
    dotted,
    e,
    east,
    english,
    entries,
    finite,
    font,
    french,
    halign,
    height,
    infinite,
    inner,
    label,
    left,
    math,
    no,
    nodes,
    north,
    only,
    ribbon,
    ribbons,
    right,
    rows,
    scale,
    separator,
    separators,
    shape,
    shifted,
    skew,
    snobs,
    valign,
    south,
%   star,
%   style,
    tabloid,
    text,
    text,
    type,
    ukrainian,
    wall,
    west,
    width,
    xoffset,
    xscale,
    yoffset,
    yscale,
  },
  moredelim=[s][keywordstyle2]{abacus star style}{=},
  moredelim=[s][keywordstyle2]{star style}{=},
  moredelim=[s][keywordstyle2]{tikz after}{=},
  moredelim=[s][keywordstyle2]{tikz before}{=},
  moredelim=[s][keywordstyle2]{text boxes}{=},
  moredelim=[s][keywordstyle2]{math boxes}{=},
  classoffset=2, % aTableau values
  keywordstyle=\color{orange},%
  morekeywords={
    A, C, DD, AA,
    beta,
    bottom,
    center,
    centre,
    contents,
    false,
    first,
    hooks,
    last,
    left,
    residues,
    right,
    row,
    top,
    true,
  },
  classoffset=3, % TikZ and LaTeX commands
  keywordstyle=\color{teal},%
  morekeywords={
    draw,
    foreach,
    node,
    small,
    tiny,
    tikz,
    tikzpicture,
    tikzset,
  },
  classoffset=4,% TikZ keys
  keywordstyle=\color{red},
  morekeywords={
    circle,
    fill,
    overlay,
    picture,
    radius,
    remember,
    style,
  },
  classoffset=5,   % commands that we want to hide :)
  keywordstyle=\color{LightSkyBlue!10},
  morekeywords={
    bigskip,
    medskip,
    newline,
    par,
    qquad,
    quad,
    smallskip,
  },
}

\newcounter{examples}
\numberwithin{examples}{subsection}
\newcommand\examplesautorefname{Example}

\NewTCBListing[use counter=examples, number within=subsection,%crefname={Example}{Examples}
]{example}{ !O{} }{%
  enhanced,
  skin=bicolor,
  colframe=RoyalBlue!70,
  colbacklower=OldLace,
  colback=LightSkyBlue!10,
  colbacktitle=RoyalBlue!70,
  attach boxed title to top right={xshift=0mm,yshift=-3.1mm},
  boxed title style={
    size=small,
    arc=1mm,
    bottom=-1mm,
    sharp corners=northwest,
    sharp corners=southeast,
  },
  sharp corners=northeast,
  parbox=false,
  lefthand width=0.35\textwidth,
  listing style=atableau,
  parbox=false,
  parskip=4mm
  sidebyside,
  sidebyside align=top seam,
  sidebyside gap=2mm,
  text and listing,
  text outside listing,
  boxsep = 0pt,
  left=0mm,
  right=2mm,
  title={\tiny\thetcbcounter},
  #1
}


\DeclareTCBListing[use counter=examples, number within=subsection,%crefname={Example}{Examples}
]{Example}{ !O{} }{%
  enhanced,
  skin=bicolor,
  colframe=RoyalBlue!50,
  colbacklower=OldLace,
  colback=LightSkyBlue!20,
  colbacktitle=RoyalBlue!70,
  breakable,
  width=\textwidth,
  attach boxed title to top right={xshift=0mm,yshift=-3.1mm},
  boxed title style={
    size=small,
    arc=1mm,
    bottom=-1mm,
    sharp corners=northwest,
    sharp corners=southeast,
  },
  title={\tiny\thetcbcounter},
  sharp corners=northeast,
  parbox=false,
  listing style=atableau,
  text and listing,
  listing above text,
  %text outside listing,
  center lower,
  #1
}

% ---------------------------------------------------------------------------
\NewDocumentCommand\set{ O{} >{\SplitArgument{1}{|}}m }{#1\{\,\SetContents{#1}#2\,#1\}}
\NewDocumentCommand\SetContents{mmm}{\IfNoValueTF{#3}{#2}{#2\,#1|\,\mathopen{}#3}}

\newcommand\T{\mathsf{t}}
\newcommand\blam{{\bm{\lambda}}}

% ---------------------------------------------------------------------------
% manual title
\makeatletter
\author{Andrew Mathas}
\usepackage{tikz}
\usetikzlibrary{
  backgrounds,
  decorations.pathmorphing,
  matrix,
  patterns,
  shadows.blur,
  shapes.geometric,
}
\tikzset{
  shadowed/.style={
    blur shadow={shadow blur steps=5},
    bottom color=RoyalBlue,
    draw=NavyBlue!70,
    shade,
    font=\normalfont\Huge\bfseries\scshape,
    %rounded corners=8pt,
    top color=LightSkyBlue!30,
  },
  boxes/.style={draw=RoyalBlue,
    fill=AliceBlue,
    font=\sffamily\small,
    inner sep=5pt,
    rectangle,
    rounded corners=8pt,
    text=MidnightBlue,
  }
}

% define the heading as a command because it contains \atableau@version
\newcommand\aTableauHeader{%
  \begin{center}
    \begin{tikzpicture}
      \aTabset{border=false}
      \draw[shadowed, rounded corners](30mm,0) rectangle node[white]{ } (\paperwidth-30mm,22mm);
      \begin{scope}[shift={(2.6,-0.2)}]
        \aTabset{scale=0.5, ribbon style={fill=LightSkyBlue!10}, inner colour=MidnightBlue}
        \Diagram(4,2) [ribbons={11,12,13,21,23,31,32,33,41,43,51,53}]{}     % A
        \Diagram(5,2) [ribbons={11,12,13,22,32,42,52}]{}                    % T
        \Diagram(6,2) [ribbons={11,12,13,21,23,31,32,33,41,43,51,53}]{}     % A
        \Diagram(7,2) [ribbons={11,12,13,21,23,31,32,33,41,43,51,52,53}]{}  % B
        \Diagram(8,2) [ribbons={11,21,31,41,51,52,53}]{}                    % L
        \Diagram(9,2) [ribbons={11,12,13,21,31,32,33,41,51,52,53}]{}        % E
        \Diagram(10,2)[ribbons={11,12,13,21,23,31,32,33,41,43,51,53}]{}     % A
        \Diagram(11,2)[ribbons={11,13,21,23,31,33,41,43,51,52,53}]{}        % U
      \end{scope}
      \node[anchor=west,boxes] at (4cm,0cm) {Andrew Mathas};
      \node[anchor=east,boxes] at (\paperwidth-4cm,0) {Version \atableau@version};
    \end{tikzpicture}
  \end{center}
}

% ----------------------------------------------------------------------
\hypersetup{
  pdfcreator={ Generated by pdfLaTeX },
  pdfinfo={
    Author  ={ Andrew Mathas },
    Keywords={ Algebraic combinatorics, representation theory, abacus, Young diagram, tableau  },
    License ={ LaTeX Project Public License v1.3c or later },
    Subject ={ LaTeXing tableaux and friends },
    Title   ={ ATableau - \atableau@version }
  },
  colorlinks=true,
  linkcolor=blue,
  urlcolor=MediumBlue,
}

\makeatother

% ----------------------------------------------------------------------
\numberwithin{equation}{subsection}
\def\equationautorefname~#1\null{(#1)\null}
\renewcommand\sectionautorefname{Chapter}
\renewcommand\subsectionautorefname{Section}
\renewcommand\subsubsectionautorefname{Subsection}

\begin{document}

  \aTableauHeader

  \begin{abstract}
    This package provides commands for drawing Young diagrams, tableaux,
    abacuses and other common objects used in algebraic combinatorics
    and representation theory.
  \end{abstract}

  \begin{center}
    \hfil
    \begin{minipage}{0.75\textwidth}
      \tableofcontents
    \end{minipage}
  \end{center}

  \begin{center}
    \aTabset{scale=0.6}
    \tikzset{
       B/.style={fill=blue},
       G/.style={fill=ForestGreen},
       R/.style={fill=red,text=white},
       Y/.style={fill=yellow},
       b/.style={ball color=blue},
       r/.style={ball color=red},
       w/.style={ball color=white},
    }
%   \Diagram{2,1^2}\qquad
    \begin{tikzpicture}
      \Tableau(0,0){[R]1[B]2,[G]3,[Y]4} \quad
      \Tableau(2.25,1)[australian]{[R]1[B]2,[G]3,[Y]4} \quad
      \Tableau(3.5,1.75)[skew={0,2}]{[Y]4[G]3[R]1,[B]2} \quad
      \Tableau(6,0)[ukrainian,skew={0,1^2}]{[B]2[R]1,[G]3,[Y]4} \quad
      \Tableau(7.5,-1)[french,skew={0,1^2}]{[B]2[R]1,[G]3,[Y]4} \quad
      \Tableau(6.0,-2.25)[ukrainian]{[R]1[G]3[Y]4,[B]2} \quad
      \Tableau(3.5,-3.0)[french]{[R]1[G]3[Y]4,[B]2} \quad
      \Tableau(2,-1)[australian]{[B]2,[R]1[G]3[Y]4} \quad
      \Abacus(4,0.5)[north, abacus bottom=---,scale=1.4]{3}{[b]9,[w]8,[r]8,[b]6,[b]6,[r]2,[b]1}
    \end{tikzpicture}
  \end{center}

  % --------------------------------------------------------------
  \section{Introduction}

  The package provides commands for drawing common objects in algebraic
  combinatorics and representation theory, together with styling options
  and a key-value interface for additional customization.  Under the
  hood, everything is drawn using \TikZ (and \LaTeX3).  These commands
  can be used either as standalone commands or as part of a
  \keyword{tikzpicture} environment.  This package grew out of my own
  research, so it does all of the things that I want it to do. On the
  other hand, it is written as flexibly as possible in the hope that it
  will draw the diagrams that others need.

  For the impatient, here is a basic example that shows how to use the main
  commands provided by the \aTableau package:

  \begin{example}
    \Abacus{4}{4^3,2,1^2,0} \qquad
    \Tableau{1239,456{10},78}
  \end{example}

  If you already know what tableaux and abacuses are, then you can
  probably work out the (basic) syntax of these two commands from this
  example and start using the package. If you do not know what tableaux
  and abacuses are, then you probably don't need this package! In any
  case, you will not find the precise mathematical definitions of these
  objects in this manual, so please consult textbooks like
  \cite{Mathas:ULect,Macdonald} if you need them. For more advanced
  usage, such as adding styling, I recommend skimming through the
  manual, and looking at the many examples.  \autoref{S:keys} gives
  quick summary of all \aTableau commands and their options.

  The \aTableau commands are intended to be easy to use and easy to
  customise. For example, partitions can be entered either as a (weakly
  decreasing list of non-negative) integers, or using exponential
  notation, or as a sequence of beta numbers (for the \keyword{\Abacus}
  command), and tableaux are entered as comma-separated words. The
  commands support the main conventions for drawing tableaux and
  diagrams.

  By way of example, the following table shows how to draw a
  Young diagram of shape $\lambda=(4,3^2,2)$ using the four tableaux
  conventions supported by \aTableau:

  \begin{center}
      \aTabset{align=centre}
      \begin{tabular}{lp{0.6\textwidth}l} \toprule
        \textcolor{aTableauMain}{Convention} &\textcolor{aTableauMain}{\aTableau command} & \textcolor{aTableauMain}{Diagram} \\ \midrule
          English    & \keyword{\Tableau[english]{1234,567,89{10},{11}{12}}}\newline(the default)
                     & \Tableau{1234,567,89{10},{11}{12}}\\[10mm]
          French     & \keyword{\Tableau[french]{1234,567,89{10},{11}{12}}}
                     & \Tableau[french]{1234,567,89{10},{11}{12}}\\[10mm]
          Ukrainian\footnotemark
                     & \keyword{\Tableau[ukrainian]{1234,567,89{10},{11}{12}}}
                     & \Tableau[ukrainian]{1234,567,89{10},{11}{12}}\\[10mm]
          Australian\footnotemark
                     & \keyword{\Tableau[australian]{1234,567,89{10},{11}{12}}}
                     & \Tableau[australian]{1234,567,89{10},{11}{12}} \\[10mm]
          \bottomrule
      \end{tabular}
      \index{english@English}
      \index{french@French}
      \index{ukrainian@Ukrainian}
      \index{australian@Australian}
      \footnotetext[1]{Some authors call this the Russian convention.}
      \footnotetext[2]{I have not seen a name for this convention in the literature. Calling this the
      \textit{Australian convention} seems apt.}
  \end{center}

  This table shows how the commands provided by \aTableau work: there
  are basic commands for drawing diagrams, and these diagrams can be
  embellished using optional arguments, which use a key-value interface.

  The different conventions for diagrams, and tableaux, are listed in
  order of (my perception of) their popularity in the literature.  By
  default, the \textit{English} convention is used, so we can omit
  \emph{english}:
  \begin{example}[lefthand width=0.4\textwidth]
  \Tableau{1234,567,89{10},{11}{12}}
  \end{example}
  for the first tableau in the table. These four conventions are used
  in exactly the same way with the \keyword{\Diagram} command:
  \begin{example}[lefthand width=0.4\textwidth]
  \Diagram{4,3,3,1} \qquad
  \Diagram[ukrainian]{4,3^2,1}
  \end{example}
  This example shows that partitions can either be typed out in full, as
  a comma-separated list of positive integers, or using exponential
  notation, which is usually shorter and easier to read.

  To use the package, add the following line to your document preamble:

  \begin{quote}
    \keyword{\usepackage[options]{atableau}}
  \end{quote}

  Here, the \textit{options} is an optional comma-separated list of
  \aTableau options, or keys --- we describe the possible options below.
  For example, to make the tableaux and Young diagrams commands use the
  \option{French} convention, by default, you could write:

  \begin{quote}
    \keyword{\usepackage[french]{atableau}}
  \end{quote}

  You can change the default options at any point in your document using
  the \keyword{\aTabset} command. Options can also be applied to
  individual commands.
  \indexcmd{aTabset}

  Each of the \aTableau commands is designed to be easy to use and easy to read,
  and it is highly customisable. Each command accepts an optional list
  of key-value options that modify the diagrams. In addition, optional
  styling can be applied to entries of a tableau and the beads in an
  abacus.  Each command can be used as a standalone object in a
  document, or they can be incorporated into a larger
  \keyword{tikzpicture} environment, making makes it possible to use
  these commands as part of more complicated diagrams.

  The general syntax of an \aTableau command is:
  \begin{quote}
    \keyword{\Command (x,y) [options] {...specifications...}}
  \end{quote}

  The $(x,y)$-Cartesian coordinates%
  \footnote{Currently, only Cartesian coordinates are supported. For
  example, it is not possible to use a named or polar coordinates.}
  are optional, being necessary if (and only if), the diagram is part of
  a~\keyword{tikzpicture} environment.  Similarly, the key-value
  \textit{options}, which control the style and appearance of the final
  diagram, are also optional.

  The possible options, or keys, for the \aTableau commands are
  described in detail below, with examples. This section emphasises only
  some of these options together with the fact that every key
  can be set ``globally'' (inside the current \LaTeX\ group), by using
  \keyword{\aTabset{...options...}}. As discussed already, the default
  options for the document can also be set via
  \keyword{\usepackage[options]{atableau}}.\indexcmd{aTabset}

  Many of the \aTableau options are specific to the particular diagrams
  being drawn. The full list of options is given in the following
  sections, and summarised in \autoref{S:keys}.  The following options
  are common to all \aTableau commands.

  \begin{options}
    \item[align]
    Sets the baseline for vertically aligning diagrams. The possible options
    are \keyword{align=top}, \keyword{align=center}, and
    \keyword{align=bottom}, which aligns the baseline of the diagram
    with the top, centre or bottom of the surrounding objects,
    respectively. By default, \aTableau are centered.

    \item[name] Set the prefix for the \TikZ \emph{named anchors} for
    the boxes and beads in \aTableau diagrams.

    \item[scale, xscale, yscale]
    Use \option{scale} to rescale all \aTableau diagrams. Use
    \option{xscale} to rescale in the $x$-direction and \option{yscale}
    to rescale in the $y$-direction.

    \item[styles]
    A short-hand for defining new \TikZ-styles for use in a diagram.

    \item[tikzpicture]
    When used without Cartesian coordinates, all \aTableau commands are
    implicitly drawn inside a \keyword{tikzpicture} environment.  Use
    \option{tikzpicture=keys} to set the optional argument of this
    environment: \keyword{\begin{tikzpicture}[ keys ]...\end{tikzpicture}}.

    \item[tikz before, tikz after]
    Use the \option{tikz before} and \option{tikz after} keys to inject \TikZ
    code into the \keyword{tikzpicture} environment, before and after
    the diagram drawn by \aTableau.
  \end{options}

  With boolean options, which are set to \textsf{true} or
  \textsf{false}, the value can typically be omitted. For example,
  \option{border} is the same as \textsf{border=true} (and \option{no
  border} is the same as \textsf{border=false}).  In all of the options,
  American spelling variations, such as \emph{center} (instead of
  \emph{centre}), \emph{color} (instead of \emph{colour}) et cetera, are
  tolerated. All of the colours in \aTableau diagrams can be changed
  using the key-value options. The names of the underlying base colours
  used by \aTableau are given in \autoref{S:Colours}.

  The next example shows how, how to use the \keyword{\Diagram} command
  inside a \keyword{tikzpicture} environment by supplying Cartesian
  coordinates.

  \begin{Example}
  % \usetikzlibrary{patterns}
  \tikzset{
    B/.style={pattern=north east lines, pattern color=blue},
    G/.style={pattern=north west lines, pattern color=ForestGreen},
  }
  \Diagram[ribbons={(G)16ccccrrr, (B)16crrcccr}]{6,5^2,2} % unlabelled diagram
  \qquad \qquad
  \begin{tikzpicture} % with labels using a tikzpicture environment
    \Diagram(0,0)[ribbons={(G)16ccccrrr, (B)16crrcccr}]{6,5^2,2}
    % add the labels
    \draw[->](1.5, 0.5)node[right]{$\alpha=(1,2)$} to [out=180,in=90]  (A-1-2.base);
    \draw[->](1.5,-2.5)node[right]{$f_\alpha=(4,2)$} to [out=180,in=270] (A-4-2.base);
    \draw[red,<->]([xshift=-1mm]A-1-1.south west)
       --node[rotate=90,above]{$l_\alpha=3$}([xshift=-1mm]A-4-1.south west);
  \end{tikzpicture}
  \end{Example}

  The diagram is drawn twice, both outside and inside a
  \keyword{tikzpicture} environment. The first diagram, which does not
  have labels, emphasizes that most of the right-hand diagram is drawn by
  the~\keyword{\Diagram} command, even though most of the commands in
  the example are \TikZ commands. In particular, the shading of the
  boxes in the \emph{$(1,2)$-hook} and \emph{$(1,2)$-rim hook} is done
  by the \option{ribbons} key. (In fact, this diagram could be drawn
  without using a \keyword{tikzpicture} environment by adding
  the \keyword{\draw}-commands to the \option{tikz after} key.)

  The top of the last example defines two \TikZ-styles, \textsf{B} and
  \text{G}, which add the \textsf{b}lue and \textsf{g}reen coloured
  hatchings of the two hooks. Inside the \keyword{tikzpicture}
  environment, the Young diagram is placed at position $(0,0)$ by the
  \keyword{\Diagram} command. The three \keyword{\draw} commands are
  used to add the three labelled arrows to the picture. Please consult
  the very readable \TikZ manual for more details on the \TikZ-commands
  in this example.

  From the viewpoint of \aTableau, the most important point of the last
  example is that the first \keyword{\Diagram} command is a standalone
  diagram, whereas the second one is part of a \keyword{tikzpicture}
  environment because it was given the Cartesian coordinate $(0,0)$. The
  second important point is that this example uses four \emph{named
  coordinates}: (\textsf{A-1-1}), (\textsf{A-1-2}), (\textsf{A-4-1}),
  and (\textsf{A-4-2}). When \aTableau draws a tableau, or a diagram, it
  creates a \TikZ named coordinate (\textsf{A-r-c}) for every box in the
  diagram, where (\textsf{A-r-c}) is the box in row~\textsf{r} and
  column~\textsf{c}. These named coordinates, or anchors, are
  \textit{only} defined for the boxes in the tableau.  Giving finer
  control, the following standard \TikZ \textit{anchors} are available:

  \begin{equation}\label{E:NodeNames}
    \begin{tikzpicture}[every node/.style={font=\tiny, text=gray}]
        \Diagram(0,0)[scale=4]{1}
        \node[label={above:(A-r-c)}] at (A-1-1){$\color{red}\bullet$};
        \node[label={above:(A-r-c.north)}] at (A-1-1.north){$\color{red}\bullet$};
        \node[label={below:(A-r-c.south)}] at (A-1-1.south){$\color{red}\bullet$};
        \node[label={right:(A-r-c.east)}] at (A-1-1.east){$\color{red}\bullet$};
        \node[label={left:(A-r-c.west)}] at (A-1-1.west){$\color{red}\bullet$};
        \node[label={above right:(A-r-c.north east)}] at (A-1-1.north east){$\color{red}\bullet$};
        \node[label={above left:(A-r-c.north west)}] at (A-1-1.north west){$\color{red}\bullet$};
        \node[label={below right:(A-r-c.south east)}] at (A-1-1.south east){$\color{red}\bullet$};
        \node[label={below left:(A-r-c.south west)}] at (A-1-1.south west){$\color{red}\bullet$};
    \end{tikzpicture}
    \qquad
    \begin{tikzpicture}[every node/.style={font=\tiny, text=gray}]
        \Diagram(0,0)[ukrainian, scale=4]{1}
        \node[label={above:(A-r-c)}] at (A-1-1){$\color{red}\bullet$};
        \node[label={above:(A-r-c.north)}] at (A-1-1.north){$\color{red}\bullet$};
        \node[label={below:(A-r-c.south)}] at (A-1-1.south){$\color{red}\bullet$};
        \node[label={right:(A-r-c.east)}] at (A-1-1.east){$\color{red}\bullet$};
        \node[label={left:(A-r-c.west)}] at (A-1-1.west){$\color{red}\bullet$};
        \node[label={above right:(A-r-c.north east)}] at (A-1-1.north east){$\color{red}\bullet$};
        \node[label={above left:(A-r-c.north west)}] at (A-1-1.north west){$\color{red}\bullet$};
        \node[label={below right:(A-r-c.south east)}] at (A-1-1.south east){$\color{red}\bullet$};
        \node[label={below left:(A-r-c.south west)}] at (A-1-1.south west){$\color{red}\bullet$};
    \end{tikzpicture}
  \end{equation}

  You can change the \textsf{A} in the name of these anchors using the
  \option{name} key. Similar anchors are created for abacus beads.
  These \textit{anchors} are a standard part of \TikZ.  If you change
  the shape of the node, then the available anchors may change; for more
  information see the \TikZ manual.

%  The previous example also shows that the \keyword{\Diagram} command
%  accepts a \option{ribbons} option, which adds one or more
%  \textit{ribbons} to the diagram. Both the ribbon and the individual
%  boxes in the ribbon can be given \TikZ styling; see
%  \autoref{S:RibbonTableaux}. All of the options to these commands are
%  described in the following sections.

  In the example above, the Cartesian coordinate $(0,0)$ is necessary
  because the \keyword{\Diagram} command is used inside a
  \keyword{tikzpicture} environment, but the choice of coordinate is not
  important in the sense that changing the coordinate will not change
  the picture. Cartesian coordinates become more meaningful when the
  \keyword{tikzpicture} environment has more components.  In the next
  example, the use of \option{name=B} makes the named
  coordinates for the first diagram take the form (\textsf{B-r-c}),
  instead of the default node names (\textsf{A-r-c}), which are used for
  the second diagram.

  \begin{example}[lefthand width=0.14\textwidth, sidebyside gap=0mm,label={Ex:ABnames}]
  % \usetikzlibrary{decorations.pathmorphing}
  \begin{tikzpicture}[wave/.style={thick,red,->,decorate,decoration=snake}]
    \aTabset{ribbon style={fill=blue!20, opacity=0.4}}
    \Diagram(0,0)[e=2,entries=residues,ribbons={13crc}]{3,2}
    \Diagram(0,-2.5)[e=2,entries=residues,ribbons={12rcr},name=B]{2^2,1}
    \draw[wave]([shift={(0,-0.05)}]A-2-1.south east)
                --([shift={(0,0.05)}]B-1-1.north east);
  \end{tikzpicture}
  \end{example}

  Notice that the ribbon styling includes \keyword{opacity=0.4}. This
  necessary because the ribbons are drawn \textit{after} the already tableau
  entries; see \autoref{SS:order}. Alternatively, these tableau entries
  can be included in the ribbon specifications, as described in
  \autoref{S:RibbonTableaux}.

  The final example in the introduction uses \keyword{\ShiftedTableau}
  inside a \emph{matrix of nodes}:

  \begin{Example}
  % \usetikzlibrary{matrix}
  \begin{tikzpicture}[scale=0.8, arr/.style={->,SteelBlue, thick}]
    \matrix (M)[matrix of nodes,row sep=4mm,column sep=4mm]{
        &    &    & \ShiftedTableau{1234,567} \\
        &    & \ShiftedTableau{1235,467}
        &    & \ShiftedTableau{1243,567}\\
        & \ShiftedTableau{1236,457}
        &    & \ShiftedTableau{1245,367}
        &    & \ShiftedTableau{1253,467}\\
      \ShiftedTableau{1237,456}
        &    & \ShiftedTableau{1246,357}
        &    & \ShiftedTableau{1254,367}\\
        & \ShiftedTableau{1247,356}\\
     };
     \draw[arr](M-1-4)--node[above]{$\sigma_4$}(M-2-3);
     \draw[arr](M-1-4)--node[above]{$\sigma_3$}(M-2-5);
     \draw[arr](M-2-3)--node[above]{$\sigma_5$}(M-3-2);
     \draw[arr](M-2-3)--node[above]{$\sigma_3$}(M-3-4);
     \draw[arr](M-2-5)--node[above]{$\sigma_4$}(M-3-6);
     \draw[arr](M-3-2)--node[above]{$\sigma_6$}(M-4-1);
     \draw[arr](M-3-2)--node[above]{$\sigma_3$}(M-4-3);
     \draw[arr](M-3-4)--node[above]{$\sigma_5$}(M-4-3);
     \draw[arr](M-3-4)--node[above]{$\sigma_4$}(M-4-5);
     \draw[arr](M-3-6)--node[above]{$\sigma_3$}(M-4-5);
     \draw[arr](M-4-1)--node[above]{$\sigma_3$}(M-5-2);
     \draw[arr](M-4-3)--node[above]{$\sigma_6$}(M-5-2);
  \end{tikzpicture}
  \end{Example}

  Notice that even though the \keyword{\SkewTableau} commands are being used inside a
  \keyword{tikzpicture} environment they do not need coordinates because
  the skew tableaux are not explicit components in the environment,
  being all (implicitly) inside \TikZ-nodes.

  The following sections describe the commands defined by the \aTableau
  package and how to use them.  We start with the \keyword{\Tableau}
  command because all of the diagram and tableau commands, except for
  \keyword{\RibbonTableau}, are derived from \keyword{\Tableau}.

  % --------------------------------------------------------------
  \section{Tableaux and Young diagrams}

    \emph{Partitions}, which are weakly decreasing sequences of
    non-negative integers, are fundamental objects in algebraic
    combinatorics and representation theory.\index{partition}  Rather
    than working with sequences of integers, it is often useful to
    visualise partitions as Young \emph{diagrams}, which are arrays of
    \emph{boxes}, or \emph{nodes}, in the plane\footnote{In this manual,
    we normally refer to the entries of tableaux and diagrams as
    \textit{boxes}, rather than \textit{nodes}. This is to avoid any ambiguity
    with \TikZ-nodes.}. A \emph{tableau} is a (Young) diagram where the
    boxes are labelled using some alphabet. Equivalently, a diagram is a
    tableau with empty labels.
    \index{young diagram@Young diagram|see{diagram}}
    \index{diagram}
    \index{tableau}
    \index{box}
    \index{node}
    \index{node|see{box}}
    \index{exponential notation}
    \index{partition!exponential notation}

    For example, $\lambda=(4,3,3,2,0,0,\dots)$ is a partition of $12$,
    since the entries sum to~$12$. It is customary to omit the zeros
    when writing partitions and to use exponents for repeated parts, so
    we can write this partition in \emph{exponential notation} as
    $\lambda=(4,3^2,2)$. Many authors identity a
    partition~$\lambda=(\lambda_1,\lambda_2,\dots)$ with its
    \emph{diagram}, which is the set $[\lambda] = \set{(r,c)|1\le
    c\le\lambda_r\text{ for }r\ge1}$.  When using the \emph{English
    convention}, the diagram of~$\lambda$ is visualised as a left
    justified array of boxes in the plane, where the first row has~$4$
    boxes, the next two lower rows have~$3$ boxes and the last row
    has~$2$ boxes. The \emph{shape} of a diagram is the partition that
    gives the number of boxes in each row. Diagrams and tableaux drawn
    using the \emph{French} convention are given by reflecting in a
    horizontal line above the diagrams, whereas the \emph{Ukrainian} and
    \emph{Australian} conventions are given by appropriately rotating
    these diagrams. All of these conventions are used in the literature,
    with some papers using more than one convention.

  % --------------------------------------------------------------
    \subsection{Tableaux}
    \indexcmd{Tableau}
    \label{S:Tableau}
    This section describes the \keyword{\Tableau} command, which draws
    tableaux or labelled diagrams. The syntax of this command is:

    \keyword{\Tableau (x,y) [options] {tableau entries}}

    where:

    \begin{options}
      \item[$(x,y)$]\index{xy@$(x,y)$} The Cartesian coordinates $(x,y)$
      are needed if, and only if, the tableau is a component of a
      \keyword{tikzpicture} environment.
      \item[options] Optional arguments. Described, with examples, below.
      \item[tableau entries]\index{tableau entries} The
      \keyword{tableau entries} are given as a comma-separated list, with commas
      separating rows and each \textit{token}, or braced-group of
      tokens, being in a separate column. As we explain below, each
      tableau entry can be prefixed by (optional) \TikZ-styling
      specifications.
    \end{options}

    We show by example how to use the \keyword{\Tableau} command,
    starting with basic usage and finishing with style. Inside
    \keyword{\Tableau}\!, the rows are separated by commas, with the
    columns given by the ``letters'' in the word for each row:

  \begin{example}
  \Tableau{ 1234, 56, 7, 8 }       \qquad
  \Tableau{ \alpha\gamma\delta q,
            xy\eta,
            \lambda\mu,
            \pi\sum }
  \end{example}

  The tableau specifications can be put on a single line, without any
  spaces. Alternatively, as shown here, spaces and line breaks can be
  added to improve readability. The one restriction is that you cannot
  have blank lines inside a \keyword{\Tableau} command. As this example
  suggests, by default, the entries in a tableau are typeset in
  mathematics-mode, but this can be changed using the
  \option{text boxes} key, which is described below.

  As the examples above show, the tableau entries can be individual
  characters, or they can be \TeX\ commands. Tableaux frequently contain
  entries that are not single characters, or given by commands. Such
  entries can be added to a tableau by enclosing them in braces:

  \begin{example}
  \Tableau{ 13{10}{11}{2x}, 2{x^2} }
  \end{example}

  There is one additional caveat for braced-entries: any
  \textit{singleton} braced entry \keyword{{...}} in a row needs to be
  \textit{double-braced}. Double-bracing is only necessary when you have
  a row that has only one column, and you have a multi-letter column
  entry. The need for double-bracing is a consequence of how \LaTeX3
  detects braced commas in comma-separated lists.
  \index{tableau entries!double-braced}
  \index{double-braced}

  The following example shows the difference between single and
  double-bracing for tableau entries.
  \index{tableau entries!double-braced}

  \begin{example}
  \Tableau{ 1345, 8{10}, {11}, {12} } \qquad
  \Tableau{ 1345, 8{10}, {{11}}, {{12}} }
  \end{example}

  The $10$'s in these tableaux do not need to be doubled-braced because
  they appear in a row of length~$2$, whichi s greater than~$1$!. In
  contrast,  because they are not doubled-braced, the~$11$ and~$12$ in
  the first tableau are both treated as being two characters in
  different columns in the first tableau. In the second tableau,
  the~$11$ and~$12$ each appear in a separate column because they are
  double-braced.

  % --------------------------------------------------------------
  \subsubsection{Adding style}
  \index{star}
  \index{*|see{star}}
  \index{tableau entries!style}
  \index{tableau entries!star}

  The \aTableau package provides several different ways to add \TikZ
  style specifications to the entries in tableaux, and to boxes in
  diagrams.  This is made possible by adding style prefixes to the
  tableau entries.  To take advantage of these styles you need to have
  at least rudimentary knowledge of \TikZ-styling. The examples in this
  manual give a good indication of what is possible.  For anything more
  exotic, please consult the \TikZ manual.

  The simplest way to change the style of an entry in a tableau is to
  add a $*$-prefix to the entry:

  \begin{example}
  \Tableau{ 1*2*3*4*5, 6*789, {10}*{11}{12}, {{13}} }
  \end{example}

  By default, the $*$-entries are given the \TikZ-styling
  \keyword{fill=}\aTableauColour{StarStyle}. You can change the default
  $*$-style using the \option{star style} key:

  \begin{example}
  \Tableau[star style={fill=red!20,draw=red,thick}]
          { 1*2*3*4*5, 6*789, {10}*{11}{12}, {{13}} }
  \end{example}

  Note that the $*$-styling overrides the default styling
  of the surrounding boxes. This is because the boxes with the default
  styling are placed first, in the order that they are entered,
  followed by boxes with custom styles are placed.

  The $*$-syntax is a quick shorthand for adding emphasis to some boxes
  in a tableau, but each of these entries will be given the same style.
  It is possible to give every box in the tableau different styles by
  putting \TikZ-styling specifications inside square brackets,
  \keyword{[...]}, before the corresponding letter in the tableau
  specification.  You can mix the $*$-syntax and the
  \keyword{[...]}-style syntax for different entries, although only one
  of these style settings can be applied to any given box.

  \begin{example}
  \Tableau[french]{
      1 [blue!20]2 [circle]3 [red]4 [cyan]5,
      6 *7 8 9,
      {10} *{11} {12},
      {{13}} }
  \end{example}

  It is not necessary to add spaces between the entries in the way that
  this example does. This is done only to make it clearer how the
  style specifications are applied to the different entries in the tableau.

  Omitting some technicalities, each box in a tableau is constructed as
  a \TikZ node, so any \TikZ-styling specifications for a node can be used.
  This example shows that some care is needed when changing the style
  because simply giving a colour changes both the colour used to
  fill the box and the text colour, which is why some of tableau entries
  in the last example appear to be blank.  If you are already familiar
  with \TikZ then you probably already know what to do. If not, then
  here is a short list of useful style specifications for \TikZ nodes:
  \begin{center}\index{fill}\index{text}\index{draw}\index{font}
     \begin{tabular}{ll}\toprule
       Style & Meaning \\\midrule
       \keyword{draw}$=\langle\text{colour}\rangle$
            & Sets the boundary colour of the node\\
       \keyword{fill}$=\langle\text{colour}\rangle$
            & Sets the fill, or background, colour of the node\\
       \keyword{font}$=\langle\text{font commands}\rangle$
            & Sets the font \\
       \keyword{opacity}$=\langle\text{value}\rangle$
            & Sets both the drawing and filling opacity to $=\langle\text{value}\rangle$\\
       \keyword{text}$=\langle\text{colour}\rangle$
            & Sets the text colour in the node \\
       \bottomrule
     \end{tabular}
  \end{center}
  In the style settings, any valid \LaTeX\ colour name can be used; see, for
  example, the \ctan{xcolor} manual. In addition, the style specifications
  \keyword{thin}\!,
  \keyword{thick}\!,
  \keyword{very thick}\!,
  \keyword{ultra thick}\!,
  \keyword{dashed}\!,
  \keyword{dotted}\!, $\dots$.
  change the border thickness, and its properties.
  \autoref{SS:TableauOptions} below describes how to use these options
  to customise the tableau style.

  If you want to apply ``complicated'' style settings, such as
  \keyword{draw=cyan,ultra thick}, which consists of a comma-separated
  list of $\TikZ-$style settings, then the entire style must be put
  inside matching square brackets and curly braces \keyword{[{...}]}.
  This is necessary to ensure that  \LaTeX\ does not get confused by the
  commas in the style setting (since commas are also used to separate
  the rows of the tableau).

  \begin{example}
  \Tableau[australian]{
      1 [fill=blue!20]2 3 [text=red]4 5,
      [{circle,fill=orange}]6 *7 8 9,
      [{draw=cyan,ultra thick}]{10} *{11} {12},
      [{dashed,draw=red,ultra thick}]{13} }
  \end{example}

  The last example shows that it is not necessary to double-brace
  singleton entries when they have a style specification.

  This example shows that modifying the borders of a box is problematic
  because boxes placed later are likely to overwrite the border (see
  \autoref{SS:order}). As a result, modifying the borders of the boxes
  is not a good way to add emphasis to a tableau,  so use this
  sparingly. In addition, the orange circle in this example looks too
  big, but it is what we asked for because the diameter of the circle is
  the horizontal width of the box. The next example shows that we get a
  better result for \textit{Australian} and \textit{Ukrainian} tableaux
  if we add a \textit{minimum size} specification.

  For complex or frequently used styles, we recommend using the
  \keyword{\tikzset} command to define the style outside of the
  \keyword{\Tableau} command. This makes your code both easier to read
  and easier to change. If you need to define a style for a single
  picture, then you can also use the \option{styles} key.

  \begin{example}[lefthand width=0.3\textwidth]
  \tikzset{
     B/.style={fill=blue!40, text=yellow},
     G/.style={fill=green!80!blue,circle,minimum size=5mm},
     R/.style={fill=red,text=white, font=\tiny},
     Y/.style={fill=yellow!20, text=blue}
  }
  \Tableau[french]{[R]1[B]2,[G]3,[Y]4} \quad
  \Tableau[ukrainian]{[R]1[B]2,[G]3,[Y]4} \newline
  \Tableau[english]{[R]1[B]2,[G]3,[Y]4} \quad
  \Tableau[australian]{[R]1[B]2,[G]3,[Y]4}
  \end{example}

  In this example, the \TikZ-styles \textsf{B}, \textsf{G} \textsf{R},
  and \textsf{Y} are applied to the tableaux entries labelled $1$, $2$,
  $3$, and $4$, respectively. Note the use of \emph{minimum size} to
  control the size of the circle. The colours used here, and throughout
  this manual, are for demonstration purposes only. I recommend against
  such garish choices in any self-respecting document!

  % --------------------------------------------------------------
  \subsubsection{Tableau coordinates}
  \index{xy@$(x,y)$}
  \index{Cartesian coordinates}

  The $(x,y)$-coordinates are required if, and only if, the
  \keyword{\Tableau}command is used inside a \keyword{tikzpicture}
  environment, in which case $(x,y)$ gives the coordinates of the
  ``outside corner'' of the box in row~$1$ and column~$1$ of the
  tableau. The following example shows how tableaux are placed using
  $(x,y)$-coordinates inside a \keyword{tikzpicture} environment. The example
  also shows that, by default, the tableau boxes are square and half a unit wide.

  \tikzset{
    add grid/.code = {
      % draw coordinate axes
      \draw[help lines, step=0.5,thin, LightGrey](-0.5,-1.5) grid (4,2.5);
      \draw[help lines, step=1,thin, Grey](-0.5,-1.5) grid (4,2.5);
      \foreach \pt in {0,...,3} {
        \node[below,font=\tiny] at (\pt,-1.5){$\pt$};
      }
      \foreach \pt in {-1,...,2} {
        \node[left, font=\tiny] at (-0.5,\pt){$\pt$};
      }
    }
  }

  \begin{example}
  \begin{tikzpicture}[add grid]
    \Tableau(0,0)    [english]   {123,45}
    \Tableau(0,0.5)  [french]    {123,45}
    \Tableau(2.5,0.5)[ukrainian] {123,45}
    \Tableau(2.5,0)  [australian]{123,45}
  \end{tikzpicture}
  \end{example}

  % --------------------------------------------------------------
  \subsubsection{Tableau keys}
  \label{SS:TableauOptions}

  The optional $*$-styles and $[\ldots]$-styles are the main mechanism
  for styling the individual boxes in a tableau. Using a key-value
  syntax, you can change aspects of the tableau produced by the
  \keyword{\Tableau} command.  The rest of this section describes these
  keys, their default values, and gives examples of how to use them.

  The options below can be applied to the \keyword{\Tableau}
  command by giving them as a comma-separated list inside square
  brackets:
  \begin{center}
    \keyword{\Tableau [options] {tableau entries}}\quad or \quad
    \keyword{\Tableau (x,y) [options] {tableau entries}}.
  \end{center}
  The options can appear in any order, with later options having
  precedence over earlier ones.

  When used inside a \keyword{\Tableau} command, the options only affect
  that particular tableau. Most of these options, or keys, can also
  be used in the \keyword{\aTabset} command, or as optional arguments in
  \keyword{\usepackage[..]{atableau}}, to change the default settings of
  all tableaux in the same \LaTeX\ group.  For example, if you put the
  command \keyword{\aTabset[ukrainian]} in the preamble of your document
  then, by default, all subsequent tableaux and Young diagrams will be drawn
  using the Ukrainian convention.

  \option[english]{english}
  \option*[]{french}
  \option*[]{ukrainian}
  \option*[]{australian}

  These four (mutually exclusive) options change the convention, or
  orientation, that is used when drawing the tableaux. Rather than
  defining these conventions precisely, we use the tired and true method
  in combinatorics of defining by example.

  \begin{example}[lefthand width=0.3\textwidth]
    \Tableau[ukrainian, styles={R={fill=red!20,draw=red}}]
    {12[R]3,45}
  \end{example}

  \begin{example}[lefthand width=0.3\textwidth]
  \tikzset{R/.style={fill=red!20, circle, draw=red, ultra thick}}
  \Tableau[french]{12[R]3,45}
  \end{example}

  \begin{example}[lefthand width=0.3\textwidth]
  \tikzset{B/.style={fill=blue!20, dashed, thick}}
  \Tableau[english]{12[B]3,45}
  \end{example}

  \begin{example}[lefthand width=0.3\textwidth]
  \tikzset{B/.style={fill=blue!20, thick, text=white}}
  \Tableau[australian]{12[B]3,45}
  \end{example}

  By default, the \option{english} convention is used to draw tableaux
  and Young diagrams. The default convention can be changed using
  \keyword{\aTabset}. Capitalised names, \keyword{Australian}\!,
  \keyword{English}\!, \keyword{French} and \keyword{Ukrainian}\!, are also
  recognised. If, for example, your document is only going to draw
  \option{french} tableaux and diagrams, then you can specify this when
  you load the package using \keyword{\usepackage[french]{atableau}}\!,
  or by adding \keyword{\aTabset{french}} to your document preamble.

  \option[centre]{align}[centre/bottom/top]

  By default, the baseline of a tableau is its centre. This can be
  changed using the \option{align} key.

  \begin{example}
    Some \Tableau[align=centre]{124,357,68} words % the default
  \end{example}

  \begin{example}
    Some \Tableau[align=top]{124,357,68} words
  \end{example}

  \begin{example}
   Some \Tableau[align=bottom]{124,357,68} words
  \end{example}

  Similarly, use \option{align} to control how tableaux are aligned
  in displayed equations.

  \begin{example}
    \aTabset{align=bottom}
    \Tableau{124,357,68}\qquad
    \Tableau{124,35}
  \end{example}

  \begin{example}
    % by default: align=centre
    \Tableau{124,357,68}\qquad
    \Tableau{124,35}
  \end{example}

  \begin{example}
    \aTabset{align=top}
    \Tableau{124,357,68}\qquad
    \Tableau{124,35}
  \end{example}

  \option[true]{border}[true/false] \newline
  \option[false]{no border}[false/true]

  The \option{border} and \option{no border} keys enable and disable
  the drawing of the (thick) border wall around a tableau. As with other boolean
  keys, \option{border} is equivalent to \option{border=true} and
  \option{no border=false}. The \option{no border} key is inverse to
  \option{border}, so \option{no border} is equivalent to
  \option{no border=true}, and to \option{border=false}.

  \begin{example}
  \Tableau[ukrainian, border=false]{123,455,674} \qquad
  \Tableau[french, no border]{123,455,674} \qquad
  \end{example}

  \option[\aTableauColour{Main}]{border colour}[any colour]
  \option*[thick,line~cap=rect]{border style}[\TikZ-styling]

  The \option{border colour} option sets the colour of the border wall,
  whereas \option{border style} sets the \TikZ-styling of the border wall.
  (So, \option{border style} can override \option{border colour}.)

  \begin{example}
  \Tableau[ukrainian, border colour=red]{123,455,674} \qquad
  \Tableau[french, border style={dashed,orange}]{123,455}
  \end{example}

  The \option{border style} key \emph{appends} any \TikZ-styles to the
  current styling of the wall.

  \option[0.5]{box height}[a decimal giving the height in \unit{cm}]
  \option*[0.5]{box width}[a decimal giving the width in \unit{cm}]

  Sets the width and height of the boxes in the tableau. The default
  height and width of the boxes is \qty{0.5}{cm} when using the
  \option{english} and \option{french} conventions and
  \qty{0.7012}{cm}, which is approximately $1/\sqrt{2}$\unit{cm}, when
  using the \option{ukrainian} and \option{australian} conventions. (In
  all cases, the default side length of the boxes is \qty{0.5}{cm}.)

  \begin{example}
  \aTabset{align=top}
  \Tableau[box height=0.5]{123,455,674} \qquad
  \Tableau[box width=0.2,ukrainian]{123,455}
  \end{example}

  See also the \option{scale}, \option{xscale} and \option{yscale}
  options.

  % nodes
  \option[none]{box fill}[any colour]

  The \option{box fill} option sets the background colour of a box in a
  tableau, just like the \textsf{fill} key for a \TikZ-node. If you use
  a dark fill colour, then you will almost certainly want to change the
  text colour using the \option{text} option -- and you may also want to
  change the colours of the border walls and inner walls using
  \option{border colour} and \option{inner colour}, respectively.

  \begin{example}
  \Tableau[box fill=blue,box text=yellow]{123,455,674} \qquad
  \Tableau[box fill=red!10]{123,455}
  \end{example}{}

  \option[]{box font}[]

  The \option{box font} key sets the font used to type the entries of a
  tableau.  By default, tableau entries are typeset as mathematics, so
  this is mainly useful for changing the font size (because, for example
  \keyword{\bfseries $1$} does not make the $1$ bold). It is only when
  you are using \option{text boxes} that font commands like
  \keyword{\itshape} and \keyword{\bfseries} will have any effect.

  \begin{example}
  \Tableau[box font=\tiny]{123,455,674} \qquad
  \Tableau[text boxes, box font=\bfseries]{123,455}
  \end{example}{}

  \option[\aTableauColour{Main}]{box text}[any colour]

  As for a \TikZ-nodes, use \option{box text} to set the default text
  colour for the entries of the tableau boxes.

  \begin{example}
  \Tableau[box text=red]{123,45} \qquad
  \Tableau[box text=blue, french]{123,45}
  \end{example}

  \option[false]{conjugate}[false/true]

  Draws the \emph{conjugate} tableau, where the rows and columns are
  swapped.

  \begin{example}
  \Tableau{123,45,67}    \qquad
  \Tableau[conjugate]{123,45,67}
  \end{example}

  \option[centre]{halign}[centre,left,right]
  \option*[centre]{valign}[bottom,centre,top]

  By default, the entries in tableaux are centered, both horizontally
  and vertically, and it is your responsibility to ensure that the
  entries fit inside the tableau boxes (you can change the box
  dimensions using the \option{box height}, \option{box width} and
  \option{scale} keys). The \option{halign} and \option{valign} keys
  provide a crude way to change the horizontal and vertical alignment of
  the box entries.

  \begin{example}
  \Tableau[halign=left]{1{11}{11},{11}1} \quad
  \Tableau[halign=centre]{1{11}{11},{11}1} \quad
  \Tableau[halign=right]{1{11}{11},{11}1}
  \end{example}

  \begin{example}
  \Tableau[valign=bottom]{qf,gpt,jb} \quad
  \Tableau[valign=centre]{qf,gpt,jb} \quad
  \Tableau[valign=top]{qf,gpt,jb}
  \end{example}

  These keys are provided for completeness only. We recommend not using them!

  \option[\aTableauColour{Inner}]{inner colour}[any colour]
  \option*[thin,line cap=rect]{inner style}[\TikZ-styling]

  The \option{inner colour} option sets the colour of the inner wall,
  whereas \option{inner style} sets the \TikZ-styling of the inner wall.
  (In particular, \option{inner style} can be used to override
  \option{inner colour}.)

  \begin{example}[label=Ex:dashed]
  \Tableau[australian, inner colour=red]{123,455,674} \qquad
  \Tableau[inner style=dashed]{123,455}
  \end{example}{}


  \index{dashed}
  \index{style!dashed}
  If you closely at the second tableau in \autoref{Ex:dashed}, you will
  notice that the dashes are not very clean. This is because, for
  example, the dashes on bottom of one box do not properly match up with
  the dashes on the top of the adjacent box below it. Rather than
  using \option{inner style=dashes} it is better to use something like
  \option{inner style=\{dash pattern=on 1pt off 2pt\}}.

  \begin{example}
  \Tableau[inner style={dash pattern=on 1pt off 2pt}]
    {123,455}
  \end{example}{}

  Use \option{inner colour=none}, to remove the inner tableau walls.

  \begin{example}
  \Tableau[ukrainian, inner colour=none]{123,45,67}
  \end{example}{}

  \option[]{label}[any character/text]
  \option*[font=\textbackslash scriptsize,text=\aTableauColour{Inner}]{label style}[\TikZ commands]

  The \option{label} key adds a label to a tableau next to the
  $(1,1)$-box. The style of the label can
  be changed using the \option{label style} key.

  \begin{example}
  \Tableau[ukrainian, label={$\mathtt{t}$}]{13,25,4} \quad
  \Tableau[french,label=0,label style={red}]{13,5} \quad
  \Tableau[label style={draw=orange,circle,inner sep=0pt},
    label=1] {12,35,5}
  \end{example}{}

  \option[true]{math boxes}[true/false]
  \option*[false]{text boxes}[true/false]

  Use the \option{math boxes} and \option{text boxes} to have the
  tableau entries typeset as either mathematics or text, respectively.
  By default, the entries of a tableau are typeset as mathematics.

  \begin{example}
  \Tableau[math boxes]{ABCD, efg, HI}\qquad% the default
  \Tableau[text boxes]{ABCD, efg, HI}
  \end{example}

  \option[A]{name}[string]

  By default, the boxes can be referenced using the node names
  \textsf{(A-1-1)}, \textsf{(A-1-2)}, \textsf{(A-1-3)}, \dots, with
  \textsf{(A-$r$-$c$)} referring to the box in row~$r$ and column~$c$.
  Use the \option{name} key to change the \emph{prefix} \textsf{A} to
  anything else that you like.  This feature is most useful when you
  have several tableaux inside a \keyword{tikzpicture} environment
  because by using \option{name} you can refer to boxes in the different
  diagrams. If you only have one tableau, then you would not normally
  need to change the default prefix for the node names. See
  \autoref{E:NodeNames} for a description of the anchor names. For
  examples using node names and anchors see \autoref{Ex:ABnames},
  \autoref{Ex:pointing} and \autoref{Ex:waves}.

  \option[]{paths}[list of path ribbon specifications]
  \option*[-]{path box}[A node entry]
  \option*[-]{path box style}[\TikZ-styling commands]
  \option*[-]{path style}[\TikZ-styling commands]

  Use the \option{paths} key to add a comma-separated list of
  \emph{ribbon paths} to the tableau. The \option{paths} key allows you
  to draw paths inside your tableau and diagrams.

  Ribbon paths are specified using the \keyword{\RibbonTableau} syntax,
  where you first specify the row and column indices of the \emph{head}
  of the ribbon, which is the unique node of maximal content in the
  ribbon, and then give a sequence of \textsf{r}'s and \textsf{c}'s
  depending on whether the row index increases, or the column index
  decreases, respectively.  As always, you have the option of adding
  style --- and you can also specify the contents of each box in the
  ribbon.  For more details about the ribbon specifications, with
  examples, see \autoref{S:RibbonTableaux}, which describes the
  \keyword{\RibbonTableau} command.

  \begin{example}
  \Tableau[styles={R={red,thick}, C={cyan,thick}},
     paths={(R)14ccrc,(C)23rcc}]{1234,567,89{10}}
  \end{example}

  The \option{ribbon box} changes the default style of every box in the
  ribbon:

  \begin{example}
  \tikzset{R/.style={red,thick},C/.style={cyan,thick}}
  \Tableau[paths={(R)14ccrc,(C)23rcc},
    ribbon style=rounded corners,
  ]{1234,567,89{10}} \qquad
  \Tableau[paths={(R)14ccrc,(C)23rcc},
    ribbon box={draw,circle}
  ]{1234,567,89{10}}
  \end{example}

  \begin{example}
  \tikzset{R/.style={red,thick},C/.style={cyan,thick}}
  \Tableau[paths={(R)14ccrc,(C)23rcc},
    ribbon box=\bullet
  ]{1234,567,89{10}}
  \end{example}


  \begin{example}
  \Diagram[ukrainian, inner style=dotted,
    styles={b={fill=blue!20,opacity=0.4},
            R={draw=red,text=red,thick},
            B={draw=blue,text=blue,thick},
    }, ribbon style={solid,thick},
    path box=\bullet,
    paths={(R)16rcrcr[b]crcrc,(blue)45r[b]crc}
  ]{7^2,5^4}
  \end{example}

  \option[]{ribbons}[list of ribbon specifications]
  \option*[]{snobs}[list of ribbon specifications]
  \option*[-]{ribbon box}[A node entry]
  \option*[-]{ribbon box style}[\TikZ-styling commands]
  \option*[draw=\aTableauColour{Inner},thin]{ribbon style}[\TikZ-styling commands]

  Use the \option{ribbons} key to add a comma-separated list of
  \emph{ribbons} to a tableau. Use \option{snobs} to add ribbons to the tableau, which are
  placed \textit{after} the border of the diagram is drawn. (Writing
  \textit{ribbons} backwards gives \textit{snob}bir.) The \option{ribbon
  style} key controls the default style of the ribbons, paths and snobs.

  When adding ribbons, or snobs, you first specify the row and column
  indices of the \emph{head} of the ribbon, which is the unique node of
  maximal content in the ribbon, and then give a sequence of
  \textsf{r}'s and \textsf{c}'s depending on whether the row index
  increases, or the column index decreases, respectively.  As always,
  you have the option of adding style --- and you can also specify the
  contents of each box in the ribbon.  For more details about the ribbon
  specifications, with examples, see \autoref{S:RibbonTableaux}, which
  describes the \keyword{\RibbonTableau} command.

  Finally, \TikZ-styling can be added to ribbons using \option{ribbon
  style} and \option{ribbon box}. The \option{ribbon style} changes the
  default style of the entire ribbon.

  \begin{example}
  \Tableau[ribbon style={fill=blue!20,opacity=0.4},
    ribbons={22rc}]{123,45,67}
  \end{example}

  Use the \option{ribbon box} option to change the default style of the
  boxes in a ribbon. For example, noting that a box is a ribbon of
  length~$1$, the following code uses ribbons of length one (that is,
  nodes), to highlight the addable nodes of this tableau.

  \begin{example}
  \Tableau[star style={fill=green!80!blue,text=white},
    ribbon box={fill=yellow,text=red},
    ribbons={15_A,24_B,42_C,51_D},
  ]{123*4,567,89*{10},*{11}}
  \end{example}

  As this example indicates, ribbons are assumed to be contained inside
  the diagram of the tableau, so they do not change the border of a
  tableau. Alternatively, if we draw this using \option{snobs} then we
  get:

  \begin{example}
  \Tableau[star style={fill=green!80!blue,text=white},
    ribbon box={fill=yellow, text=red},
    snobs={15_A,24_B,42_C,51_D},
  ]{123*4,567,89*{10},*{11}}
  \end{example}

  The difference between these two pictures is that in the second
  picture the nodes in the \option{snobs} are drawn over the tableau
  border, causing the border to disappear for these nodes.  For this
  reason, in most cases you should normally avoid \option{snobs} and use
  \option{ribbons}.


  \option[1]{scale}[a decimal number]
  \option*[1]{xscale}[a decimal number]
  \option*[1]{yscale}[a decimal number]

  By design, boxes in tableaux do not automatically resize to fit
  their contents. For example, consider:

  \begin{example}
  \Tableau{ 13{10}{11}{1+x}, 2{1+x} }
  \end{example}

  This is unlikely to be the desired output! The options \option{scale},
  \option{xscale} and \option{yscale} can be used to rescale the boxes
  in tableaux and diagrams. The names are slightly misleading because
  \option{xscale} rescales in the direction of increasing column index
  and \option{yscale} rescales in the direction of increasing row index.

  \begin{example}
  \Tableau[scale=2]{ 13{10}{11}{1+x}, 2{1+x} }
  \end{example}

  \begin{example}
  \Tableau[xscale=2]{ 13{10}{11}{1+x}, 2{1+x} }
  \end{example}

  When using the \textsf{australian} and \textsf{ukrainian} conventions,
  \option{xscale} and \option{yscale} scale in both the \textsf{x}
  direction and the \textsf{y}-direction, reflecting how these tableaux
  grow with increasing column and row index, respectively.

  \begin{example}
  \Tableau[ukrainian, xscale=2]{ 13{10}{11}{1+x}, 2{1+x} }
  \end{example}

  \begin{example}
  \Tableau[australian,yscale=2]{ 13{10}{11}{1+x},2{1+x} }
  \end{example}

  \begin{danger}
    The options, \option{scale}, \option{xscale}, and \option{yscale},
    affect all \aTableau diagrams, including tableaux, Young diagrams
    and abacuses. If you want to use \keyword{\aTabset} to change the
    default sizes of the diagrams and tableaux in your document, then it
    is probably better to use the \option{box height} and \option{box
    width} options.
  \end{danger}

  \option[false]{shifted}[true/false]

  Set to \textsf{true} for a shifted tableau or shifted diagram. Shifted
  tableaux, and shifted diagrams, are discussed in more detail in
  \autoref{S:Shifted}, which describes the \keyword{\ShiftedDiagram} and
  \keyword{\ShiftedTableau} commands.

  \begin{example}
  \Tableau[shifted]{123,45} \qquad
  \Diagram[shifted]{3,2^2}
  \end{example}

  See \autoref{S:Shifted} for the options specific to shifted tableaux and
  shifted diagrams.

  \option[(0)]{skew}[a partition]

  Specify the skew shape for a skew tableau or skew diagram. Skew
  tableaux, and skew diagrams, are discussed in more detail in
  \autoref{S:Skew}, which describes the \keyword{\SkewDiagram} and
  \keyword{\SkewTableau} commands.

  \begin{example}
  \Tableau[skew={2}]{123,45} \qquad
  \Diagram[skew={2^2,1}]{3,2^2}
  \end{example}

  See \autoref{S:Skew} for the options specific to skew tableaux and skew diagrams.

  \option[fill=\aTableauColour{StarStyle}]{star style}[\TikZ-styling]

  Use the \option{star style} to add to the style of the starred entries
  of a tableau. (In \TikZ parlance, \option{star style} \emph{appends}
  appends these styles to the default \option{star style}.)

  \begin{example}
  \Tableau[star style={text=magenta,
     draw=cyan, thick}]{1*2*3,4*5} \quad
  \Tableau[star style={fill=orange!50}]{1*2*3,4*5}
  \end{example}

  Note that the tableau border is drawn \textit{after} the
  \option{star style} is applied. You can use \option{snobs} to draw on
  top of the border.

  \option[-]{styles}[List of \TikZ style specifications]

  The \option{styles} key is a shorthand for defining \TikZ-styles that
  are only used in the current picture. For example, instead of writing

  \begin{example}
  \tikzset{
     B/.style={fill=blue!40, text=yellow},
     G/.style={fill=green!80!blue,circle,minimum size=5mm},
     R/.style={fill=red,text=white, font=\tiny},
     Y/.style={fill=yellow!20, text=blue}
  }
  \Tableau[french]{[R]1[B]2,[G]3,[Y]4}
  \end{example}

  you can save a little bit of typing by using the \option{styles} key:

  \begin{example}
  \Tableau[french, styles={
     B={fill=blue!40, text=yellow},
     G={fill=green!80!blue,circle,minimum size=5mm},
     R={fill=red,text=white, font=\tiny},
     Y={fill=yellow!20, text=blue},
  }]{[R]1[B]2,[G]3,[Y]4}
  \end{example}

  Styles defined this way will only be available in the current picture.
  Use \keyword{\tikzset} to define styles that will be used more than
  once.

  \option[false]{tabloid}[true/false]

  Use the \option{tabloid} key to draw a tabloid. This key is discussed in
  more detail in \autoref{S:Tabloid}, which describes the
  \keyword{\Tabloid} command.

  \begin{example}
  \Tableau[tabloid]{123,45} \qquad
  \Diagram[tabloid]{3,2^2}
  \end{example}

  See \autoref{S:Tabloid} for the options specific to tabloids.

  \option[]{tikz before}[\TikZ commands]
  \option*[]{tikz after}[\TikZ commands]

  These keys inject \TikZ code into the underlying \keyword{tikzpicture}
  environment, where the tableau is constructed, before and after the
  \keyword{\Tableau} command, respectively.

  \begin{example}[lefthand width=0.24\textwidth]
  \Tableau[
   tikz before={\draw[help lines,step=0.5](-0.5,-2)grid(2,0.5);},
   tikz after={\draw[ultra thick,red]
                 (A-1-3.north east)--(A-1-3.south east)
                 --(A-2-1.north east)--(A-3-1.south east)
                 --(A-3-1.south west);
   }]{134,567,89}
  \end{example}

  Both before and after hooks are provided because the order in which
  you place \TikZ commands can affect the drawing because later commands
  are drawn over the top of earlier ones. Note that the \textit{before}
  code cannot use the named nodes \textsf{A-r-c} because this code is
  executed before these nodes are constructed, which happens when the
  tableau is drawn. For more examples, see \autoref{SS:order}.

  \option[]{tikzpicture}[\TikZ-keys]

  This command adds an optional argument to the underlying
  \keyword{tikzpicture} environment, which contains the tableau. The
  \option{tikzpicture} option is ignored  when the \keyword{\Tableau}
  command is equipped with $(x,y)$-coordinates.

  As a first example, we can use \keyword{tikzpicture={rotate=30}}
  to rotate a tableau by 90 degrees:

  \begin{example}
  \Tableau[tikzpicture={rotate=90}]{123,45} \qquad
  \begin{tikzpicture}[rotate=90]
   \Tableau(0,0){123,45}
  \end{tikzpicture}
  \end{example}

  The two tableaux constructions in this example are equivalent. An
  oddity with both of these examples is that the numbers in the tableaux
  have not been rotated, which is because the \TikZ \emph{rotate} key
  does not affect component objects, such as nodes, inside a \TikZ
  picture. You can rotate the entire picture using the
  \textit{transform canvas} key:

  \vspace*{15mm}

  \begin{example}[valign=top, lefthand width=0.3\textwidth]
  \Tableau[tikzpicture={transform canvas={rotate=90}}]{123,45}
  \end{example}

  A more interesting example is that by using
  \option{tikzpicture=remember picture} we can add annotations to
  a tableau. For example, consider:

  \begin{example}[lefthand width=0.3\textwidth, label={Ex:pointing}]
  \Tableau[ukrainian, name=A,
    tikzpicture={remember picture}]
    { 1[fill=blue!20]23[text=red]45,
      6*78[{draw=cyan,ultra thick}]9,
      [{circle,fill=orange}]{10}*{11}{12},
      [{dashed,draw=red,ultra thick}]{13}
    }
  \end{example}

  Since \option{name}=A, the nodes in this tableau are referenced as
  \textsf{(A-1-1)}, \textsf{(A-1-2)}, \textsf{(A-1-3)}, \dots. As the
  example uses \textit{remember picture}, other \keyword{tikzpicture}
  environments can reference the node names in last tableau, which
  allows us to do things like this:

  \vspace*{3mm}

  \begin{example}[lefthand width=0.3\textwidth]
  \tikz[remember picture, overlay]
   \draw[very thick, ->,red]
     (0,0) node[right,align=left]
        {This circle is too big!\\Use minimum size=5mm}
     to [out=135, in=225](A-3-1);
  \end{example}

  % --------------------------------------------------------------
  \subsubsection{Compositions}
  \index{composition}

  As we have defined them, tableaux are always of \textit{partition}
  shape, in the sense that the lengths of the rows is a weakly
  decreasing sequence. In fact, the \keyword{\Tableau} command also
  accepts tableaux of \emph{composition} shape, where the lengths of the
  rows are not necessarily in decreasing order:

  \begin{example}
  \Tableau{ 45,2751,31 } \qquad
  \SkewTableau{1,2}{ 45,27,31 }
  \end{example}

  Even though it is possible to draw compositions, and tableaux of
  composition shape, compositions are not supported in the sense that
  many of the options/keys assume that the diagrams are of partition
  shape.  In addition, some options assume that tableaux and diagrams do
  not contain empty rows, and that the diagrams are \textit{connected}.
  (For disconnected tableaux and diagrams, see the
  \keyword{\Multidiagram} and \keyword{\Multitableau} commands in
  \autoref{S:Multitableau}.)

  % --------------------------------------------------------------
  \subsubsection{Drawing order}
  \label{SS:order}
  \index{tableau!drawing order}

  When \TikZ constructs a picture, later objects are drawn over the top
  of earlier ones, which can obscure earlier features. Consequently,
  for more complicated diagrams and tableaux it helps to know the order
  in which the different parts of these diagrams are drawn, which is the
  following:
  \begin{itemize}
    \item First, the tableau entries that use the default styling are
    placed, in the order that they appear in the \textit{tableau
    specifications}.
    \item Secondly, the styled tableau entries are placed, in the order
    that they appear in the \textit{tableau specifications}.
    \item Next, the nodes in any \option{ribbons} and ribbon
    \option{paths} are placed, again in the order that the ribbons are
    listed. For each ribbon, first the border of the ribbon is drawn,
    together with any styling for the ribbon, and then the boxes in the
    ribbon, together with any styling, are added.
    \item When enabled by \option{skew border}, the skew border is
    drawn, after which the border of the tableau is drawn.
    \item The \option{dotted rows} and \option{dotted columns} keys are
    applied to replace the specified rows and columns with dots.
    \item Finally, any \option{snobs} are drawn, in the order that they are listed.
  \end{itemize}

  All of the tableau and Young diagram commands use this drawing order.

  % --------------------------------------------------------------
  \subsubsection{Special characters}
  \index{tableau!special characters}
  \index{tableau!comma}
  \index{tableau!*}
  \index{tableau![}

  The characters  \textsf{[]}, \textsf{,}, and \textsf{*} have
  special meanings in the \textit{tableau specifications}. Enclose these characters in
  braces when you want to use these characters as entries in a tableau:

  \begin{example}
  \Tableau{ 13{,}5], 8{[}, {{*}} }
  \end{example}

  There is no need to enclose~\keyword{]} in braces because it only
  becomes special when it is preceded by a matching~\keyword{[}
  character.

  % --------------------------------------------------------------
  \subsection{Young diagrams}
  \label{S:Diagram}
  \indexcmd{Diagram}
  \index{young diagram@Young diagram|see{diagram}}
  \index{diagram}
  \index{diagram}
  \index{partition!diagram}

  A \emph{Young diagram}, or simply a \emph{diagram}, is an unlabelled
  tableau. Diagrams can be drawn using the \keyword{\Tableau} command:

  \begin{example}
  \Tableau{~~~,~~~,~~,~}
  \end{example}

  This approach works, but it is cumbersome, hard to proofread, and easy to miscount.
  For this reason, \aTableau provides the \keyword{\Diagram} command.  The
  \keyword{\Diagram} command uses almost the same syntax as the
  \keyword{\Tableau} command:

  \keyword{\Diagram (x,y) [options] {partition}}

  As with the \keyword{\Tableau} command, the $(x,y)$-coordinates are
  needed if, and only if, the diagram is inside a \keyword{tikzpicture}
  environment.  The \keyword{\Diagram} command allows the
  \emph{partition} to be specified as either a comma-separated list of
  \emph{weakly decreasing positive integers}, or by using \emph{exponential
  notation}:
  \index{exponential notation}
  \index{partition!exponential notation}
  \index{diagram!exponential notation}

  \begin{example}
  \Diagram{4,3^2,1^3} \qquad
  \Diagram{4,3,3,1}
  \end{example}

  Internally, \keyword{\Diagram} actually does something like the first
  example in this section, so all of the options for the
  \keyword{\Tableau} command can be used with \keyword{\Diagram}. Rather
  than repeating all of the \keyword{\Tableau} options in this section,
  we highlight the more interesting options together with some new,
  diagram specific, options.

  \begin{samepage}
  Just like the \keyword{\Tableau} command, \keyword{\Diagram} supports the
  four different conventions for diagrams, with \option{english} being
  the default:

  \option[]{english}
  \option*[]{french}
  \option*[]{ukrainian}
  \option*[english]{australian}
  \end{samepage}

  \begin{example}
  \Diagram[australian]{3,2,1} \qquad
  \Diagram[australian]{3,1^3}
  \end{example}

  \begin{example}
  % English is the default convention
  \Diagram[english]{3,2,1} \qquad
  \Diagram{3,1^3}
  \end{example}

  \begin{example}
  \Diagram[french]{3,2,1} \qquad
  \Diagram[french]{3,1^3}
  \end{example}

  \begin{example}
  \Diagram[ukrainian]{3,2,1} \qquad
  \Diagram[ukrainian]{3,1^3}
  \end{example}

  \option[true]{border}[true/false]\newline
  \option[false]{no border}[false/true]

  If \option{border} is true, which it is by default, then the border of
  the tableau is drawn.  If \option{border} is false, then the border of
  the tableau is not drawn. Notice that the border refers only to the
  outside border of the diagram, and not to the internal borders of the
  boxes on the diagram, which can be disabled using
  \option{no boxes}.

  \begin{example}
  \Diagram[border=false]{3,2,1} \qquad
  \Diagram[no border, french]{3^2,1}
  \end{example}

  The \option{no border} option, and similar options, are provided only
  for completeness because it is the inverse of \option{border}. That
  is, \option{no border} is equivalent to \option{border=false}, and
  \option{no border=false} is equivalent to \option{border=true}.

  \option[true]{boxes}[true/false]
  \option*[false]{no boxes}[false/true]

  The \option{boxes} and \option{no boxes} keys control whether or not
  the internal wall around the boxes are drawn, with these two keys
  being inverses of each other. By default, \option{boxes} is true, so
  the internal boxes are drawn.  When \option{no boxes} is in force, the
  internal walls around boxes are not drawn.

  \begin{example}
  \Diagram[no boxes]{3,2,1} \qquad
  \Tableau[french, no boxes, no border]{123,45}
  \end{example}

  \option[false]{conjugate}[false/true]

  Draws the conjugate diagram, which has the rows and columns
  interchanged.

  \begin{example}
  \Diagram[conjugate]{3,2,2} \qquad
  \Diagram[ukrainian, conjugate]{2,1^3}
  \end{example}

  \option[]{dotted columns}[comma separated list of columns]
  \option*[]{dotted rows}[comma separated list of rows]

  The \option{dotted rows} and \option{dotted columns} keys can be used
  to draw  diagrams where the specified rows and columns are
  replaced with dots. This makes it possible to draw \emph{generic}
  diagrams, where the number of rows and columns is not fully
  specified.  Instead of \option{dotted columns}, you can use the
  equivalent short-hand key \option{dotted cols}.

  \begin{example}
  \aTabset{scale=0.8}
  \Diagram[dotted rows={2,4,5}]{4^2,2^2,1^3} \qquad
  \Diagram[dotted columns={5,3,4},
    no boxes] {6,5,4,3,2,1}
  \end{example}

  As shown above, when row and columns indices are in increasing
  \textit{consecutive} order, then the corresponding rows or columns are
  replaced as a block. Non-consecutive indices are treated separately.

  \begin{example}
  \aTabset{scale=0.8, no boxes}
  \Diagram[dotted rows={4,5,3}] {6,5,5,5,2,1}
  \Diagram[dotted cols={5,3,4}] {6,5,5,5,2,1}
  \end{example}

  \index{tableau~dotted rows}
  \index{tableau~dotted columns}
  The \option{dotted rows} and \option{dotted columns} keys work by
  overwriting the content on the specified rows and columns, so
  anything that was drawn in these rows and columns will disappear.  The
  \option{dotted rows} and \option{dotted columns} keys can be used with
  the \keyword{\Tableau} command, with the caveat that this will remove
  all boxes, with their contents, ghat are in the specified rows and columns.

  When the \option{dotted rows} and \option{dotted columns} keys are
  used together, the \option{dotted rows} are applied first.

  \begin{example}
  \Diagram[scale=0.8, no boxes,
    dotted rows={4,5},
    dotted cols={4,5},
  ] {6,5,5,5,2,1}
  \end{example}

  When using these two keys together, you need to be careful when
  choosing which rows and columns are removed because, otherwise,
  artifacts can remain. Ideally, the endpoints of the rows and columns
  being removed should not overlap. For example, the circled horizontal
  dots below are a ``user error'', not a bug, because these dots come
  from trying to use \option{dotted rows} to remove row three:

  \begin{example}
  \Diagram[scale=0.8, no boxes,
    dotted rows={4,5,3}, dotted cols={4,5,3},
    tikz after = {\draw[red] (1,-1.6) circle(0.3);}
  ] {6,5,5,5,2,1}
  \end{example}


  The \option{dotted rows} and \option{dotted columns} keys are not
  designed to be used with the \option{conjugate} key.

  \option[]{ribbons}[ribbon specification]\newline
  \option*[]{paths}[ribbon specification]
  \option*[]{snobs}[ribbon specification]

  Use \option{ribbons}, \option{paths} and \option{snobs} to add
  ribbons, ribbon paths and snobs to a diagram, respectively. The
  \option{snobs} are drawn after the border of the diagram.

  \begin{example}
  \Diagram[french, ribbons={*22*c*r*r}]{3,2^2,1}
  \end{example}

  A description of the ribbon specifications, with examples, can be
  found in \autoref{S:RibbonTableaux}, which describes the
  \keyword{\RibbonTableau} command.

  % --------------------------------------------------------------
  \subsubsection{Diagrams with entries}\label{SS:entries}
  \index{contents}
  \index{first tableau}
  \index{hooks}
  \index{last tableau}
  \index{residues}
  \index{first tableau}
  \index{tableau!contents}
  \index{tableau!first}
  \index{tableau!hooks}
  \index{tableau!last}
  \index{tableau!residues}

  The \option{entries} option provides a shortcut for drawing some common
  tableaux of a specified shape.

  \option[]{entries}[contents,first,hooks,last,residues]

  The possible choices are:

  \begin{itemize}

    \item\option{entries=first} print the \emph{first}
    \textbf{standard} tableau of this shape, with respect to the Bruhat
    order. This is the tableau that has the numbers $1,2\dots,n$ entered
    in order from top left to right along down successive rows (with
    appropriate modifications for the non-English conventions).

    \index{first tableau}
    \index{tableau!first}
  \begin{example}
  \Diagram[entries=first]{3,2,2} \qquad
  \Diagram[ukrainian, entries=first]{3^2,2}
  \end{example}

    \item\option{entries=last} print the \emph{last} \textbf{standard}
    tableau of this shape, with respect to the Bruhat order. This is the
    tableau that has the numbers $1,2\dots,n$ entered in order from top
    to bottom down successive columns (with appropriate modifications
    for the non-English conventions).

    \index{last tableau}
    \index{tableau!last}
  \begin{example}
  \Diagram[entries=last]{3,2,2} \qquad
  \Diagram[australian,entries=last]{2^2,1}
  \end{example}

    \item\option{entries=hooks} print the diagram where each box is
    labelled by the corresponding \emph{hook length}. If $\lambda$ is a
    partition and $\lambda'$ is its conjugate partition then the hook
    length of the box in row~$i$ and column~$j$ is
    $\lambda_i-i+\lambda'_j-j+1$.

    \index{tableau!hook lengths}
    \index{hook lengths}
  \begin{example}
  \Diagram[entries=hooks]{3,2,2} \qquad
  \Diagram[ukrainian,entries=hooks]{2^2,1}
  \end{example}

  \item\option{entries=contents} where each box is
    labelled by its \emph{content}, which is the row index minus the
    column index.

  \begin{example}
  \Diagram[entries=contents]{3,2,1} \qquad
  \Diagram[french,entries=contents]{2^2,1}
  \end{example}

  \smallskip\noindent Inside a tableau, the default minus sign for a
  negative number looks too long, so \aTableau uses
  \keyword{\shortminus} for negative contents. For example, it prints
  \keyword{\shortminus 1} instead of \keyword{-1}, which look like
  $\shortminus1$ and $-1$, respectively.\indexcmd{shortminus}

  \item\option{entries=residues} print the diagram where each box is
  labelled by its \emph{residue}, which is the row index minus the
  column index modulo an integer~$e\ge2$, which must also be supplied.

    \index{residue}
    \index{tableau!residues}
    \index{affine quiver}
  \begin{example}
  \Diagram[entries=residues, e=2]{3,2,1} \qquad
  \Diagram[french, entries=residues, e=3]{3,2,1}
  \end{example}

  \noindent\AddOptionLink{cartan}\AddOptionLink{e}
    By default, residue sequences for affine type $A^{(1)}_e$, or the symmetric
    group and friends, are given. In addition, residues in affine types
    $C^{(1)}_e$, $A^{(2)}_{2e}$ and $D^{(2)}_e$, which can be accessed
    using \option{cartan=C}, \option{cartan=AA}, and \option{cartan=DD},
    respectively.

    \smallskip
  \begin{example}
  % affine type C
  \Diagram[french,entries=residues,
    e=2, cartan=C] {8,4,2}
  \end{example}

  \begin{example}
  % twisted affine type A
  \Diagram[ukrainian, entries=residues,
     e=2, cartan=AA] {8,4,2}
  \end{example}

  \begin{example}
  % twisted affine type D
  \Diagram[australian, entries=residues,
    e=2, cartan=DD] {8,4,2}
  \end{example}

  \end{itemize}

  % --------------------------------------------------------------
  \subsection{Skew tableaux and skew diagrams}
  \label{S:Skew}
  \indexcmd{SkewTableau}
  \indexcmd{SkewDiagram}
  \index{diagram!skew}
  \index{partition!skew}
  \index{tableau!skew}

  A partition $\mu$ is \emph{contained} in another partition $\lambda$, which
  is written as~$\mu\subseteq\lambda$, if $\mu_k\le\lambda_k$, for
  $k\ge0$. If $\mu\subseteq\lambda$ then the \emph{skew partition}
  $\lambda/\mu=\set{(r,c)\in\lambda|(r,c)\notin\mu}$ is the set of nodes
  that are in~$\lambda$ and not in~$\mu$. In this manual, $\mu$ is
  the \emph{inner shape} and $\lambda/\mu$ is the outer shape. A
  \emph{skew tableau} is a labelling of the nodes in the diagram of a
  skew partition. Skew partitions and skew tableau can be drawn using
  the commands:

  \keyword{\SkewDiagram (x,y) [options] {inner shape} {outer shape}}\newline
  \keyword{\SkewTableau (x,y) [options] {inner shape} {skew tableau specifications}}

  \index{exponential notation}
  As with the previous commands, the $(x,y)$--coordinates should be given
  if, and only if, the picture is inside a \keyword{tikzpicture}
  environment.  The inner and outer shapes can either be given as a
  comma-separated list of non-negative integers, or in exponential notation.

  Skew tableau and skew diagrams should always be connected. Use
  \keyword{\Multidiagram} and \keyword{\Multitableau} to draw
  disconnected diagrams.

  In fact, the \keyword{\SkewTableau} is just an alias for the
  \keyword{\Tableau}, using the \option{skew} key to set the inner
  shape. For this reason, all of the options for the \keyword{\Tableau}
  command can be used with \keyword{\SkewTableau}. The entries in a
  \keyword{\SkewTableau} are specified in exactly the same way as in the
  \keyword{\Tableau} command. In particular, the entries of skew
  tableaux can, optionally, be given style prefixes, both using a~$*$ to
  add the current \option{star style}, or arbitrary \TikZ-styling using
  \keyword{[...]}.

  \begin{example}
  \tikzset{R/.style={fill=red!20,text=red}}
  \SkewTableau[french]{1^2}{13,5*7,[R]79} \qquad
  \Tableau[french,skew={1^2}]{13,5*7,[R]79}
  \end{example}

  Similarly, the \keyword{\SkewDiagram} command is an alias for the
  \keyword{\Diagram} command, with a \option{skew} key.

  \begin{example}
  \SkewDiagram[french]{1^2}{2^3} \qquad
  \Diagram[french,skew={1^2}]{2^3}
  \end{example}

  As the \keyword{\SkewTableau} and \keyword{\SkewTableaua} commands
  are shortcuts, all of the options for the \keyword{\Tableau} and
  \keyword{\Diagram} commands can be used with the
  \keyword{\SkewTableau} and \keyword{\SkewDiagram} commands,
  respectively. In addition, the following options are supported:

  \option[false]{skew border}[true/false]
  \option*[true]{no skew border}[false/true]

  These two keys are inverse to each other.  When
  \option{skew border} is \textsf{true}, the border of the (inner) skew
  shape is drawn.

  \begin{example}
  \tikzset{R/.style={fill=red!20,circle}}
  \SkewTableau[skew border]{2,1^2}{12[R]3,45,67}
  \SkewTableau[french,skew border]{2,1^2}{12[R]3,45,67}
  \end{example}

  Note that \option{skew border} only draws the border of the skew shape
  and not the boxes inside the inner skew shape. Use \option{skew boxes}
  to draw the interior walls of the boxes in the skew shape.

  \option[draw=\aTableauColour{Skew}, fill=\aTableauColour{SkewFill}, thick]{skew border style}[\TikZ-styling]

  Use \option{skew border style} to change the style of the skew border.
  Since the skew border is only drawn when \option{skew border} is set,
  the \option{skew border style} does not have any effect unless
  \option{skew border} has been set to \textsf{true}.

  \begin{example}
  \SkewTableau[skew border style={draw=yellow},
      skew border]{2,1^2}{123,45,67} \qquad
  \SkewDiagram[skew border style={dashed,fill=red!10},
      skew border]{1^2}{2^3}
  \end{example}

  \option[false]{skew boxes}[true/false]
  \option*[thin, fill=\aTableauColour{SkewFill}]{skew box style}[\TikZ-styling]

  The \option{skew boxes} key draws the inner walls in the inside the
  inner partition of a skew shape. Use \option{skew box style} to change
  the default shading of these boxes.

  \begin{example}
  \SkewTableau[skew boxes] {2,1^2}{123,45,67}
  \SkewTableau[skew boxes,
    skew box style={dash pattern=on 1pt off 2pt}
  ] {2,1^2}{123,45,67,89}
  \end{example}

  Using the options \option{skew border} and the \option{skew boxes}
  together gives the skew (inner) shape both inner and outer borders.

  \begin{example}
  \SkewTableau[skew border, skew boxes] {2^2,1}{123,45,67}
  \end{example}

  % --------------------------------------------------------------
  \subsection{Shifted tableaux and shifted diagrams}
  \label{S:Shifted}
  \indexcmd{ShiftedTableau}
  \indexcmd{ShiftedDiagram}
  \index{diagram!shifted}
  \index{strict partition}
  \index{partition!strict}
  \index{shifted tableau}
  \index{tableau!shifted }

  \emph{Strict partitions}, which have strictly increasing parts, and
  \emph{shifted tableaux}, which are of strict partition shape, appear
  in several places in representation theory, such as in the study of
  projective representations of the symmetric groups. These tableaux and
  diagrams are drawn with row~$r$ shifted by $(r-1)$-units along the
  row, so that the first box in each row has content~$0$. These diagrams
  and tableaux can be drawn using the following commands:

  \keyword{\ShiftedDiagram (x,y) [options] {partition }}\newline
  \keyword{\ShiftedTableau (x,y) [options] {tableau specification}}

  As usual, the $(x,y)$-coordinates are necessary if, and only if, these
  commands are used inside a \keyword{tikzpicture} environment. The
  partition in a~\keyword{\ShiftedDiagram} can be given using
  exponential notation and the tableau specification for a
  \keyword{\ShiftedTableau} can include the usual optional style
  prefixes.

  \begin{example}
  \tikzset{R/.style={fill=red!20,circle}}
  \ShiftedTableau{12[R]3,45,*6}  \qquad
  \ShiftedDiagram[french]{3,2,1}
  \end{example}

  In the literature,  shifted tableaux and shifted diagrams almost
  always have strict partition shape, however, this is not enforced by
  these commands. Under the hood, the \keyword{\ShiftedTableau} is the
  \keyword{\Tableau} command with the \option{shifted} option set
  to true. Similarly, \keyword{\ShiftedDiagram} is the same as using
  the \keyword{\Diagram} command with the \option{shifted} option. Consequently,
  all of the options for the \keyword{\Tableau} and \keyword{\Diagram}
  commands can be used with \keyword{\ShiftedTableau} and
  \keyword{\ShiftedDiagram}, respectively.  In particular, options like
  \option{skew boxes} can be used to highlight the shifted part of the
  diagram

  \begin{example}
  \ShiftedTableau[skew boxes]{1*23,4*5} \quad
  \ShiftedDiagram[skew border]{3,2}
  \end{example}

  The \option{entries} key works as expected for shifted diagrams:

  \begin{Example}
  \ShiftedDiagram[entries=contents]{3,2,1} \qquad
  \ShiftedDiagram[entries=first]{4,2,1} \qquad
  \ShiftedDiagram[entries=hooks]{4,2,1} \qquad
  \ShiftedDiagram[entries=last]{4,2,1} \qquad
  \ShiftedDiagram[entries=residues,e=3]{4,2,1}
  \end{Example}

  The definition of hook lengths for shifted diagrams can be found, for
  example, in \cite{Konvalinka:ShiftedHookLengths}!

  % --------------------------------------------------------------
  \subsection{Tabloids}
  \label{S:Tabloid}
  \indexcmd{Tabloid}

  A \emph{tabloid} is an equivalence class of tableau, where two tableaux
  are equivalent if they have the same entries in each row, up to a
  permutation. In the literature, tabloids are usually drawn with lines
  above and below each row, and without side borders. Tabloids can be
  drawn with the \keyword{\Tabloid} command.

  \keyword{\Tabloid (x,y) [options] {partition }}

  The \keyword{\Tabloid} command functions in the same way as the
  \keyword{\Tableau} command, except that it draws tabloids. In fact,
  the \keyword{\Tabloid} is a special case of the \keyword{\Tableau}
  command with the \option{tabloid} option set.

  \begin{example}
  \tikzset{R/.style={fill=red!20,circle,minimum size=5mm}}
  \Tabloid[ukrainian]{12[R]3,45}\quad
  \Tabloid[english]  {12[R]3,45}\quad
  \Tabloid[french]   {12[R]3,45}
  \end{example}

  The \aTableau package does not provide a dedicated command for tabloid
  diagrams, however, they can be drawn using the \keyword{\Diagram}
  command together with the \option{tabloid} option:

  \begin{example}
  \Diagram[tabloid]{3^2,1} \qquad
  \Diagram[tabloid,french]{3,1^2}
  \end{example}

  Some authors work with \emph{column tabloids}. Such tableaux do not
  have a dedicated \aTableau command, however, they can be drawn using the
  \option{conjugate} option:  \index{tabloids!column}

  \begin{example}
  \Tabloid[conjugate]{123,4} \qquad
  \Diagram[conjugate,tabloid]{3,1} \qquad
  \end{example}

  Similarly, skew tabloids and shifted tabloids can be drawn using the \option{skew}
  option.
  \label{tabloids!skew}

  \begin{example}
  \Tabloid[skew={2,1}]{19{11},29{10},6} \qquad
  \Tabloid[conjugate,skew={0,1,2}]{19{11}7,29{10},6}
  \end{example}


  % --------------------------------------------------------------
  \subsection{Ribbon tableaux}\label{S:RibbonTableaux}
  \indexcmd{RibbonTableau}
  \index{ribbon!head}
  \index{tableau!ribbon tableau}

  A \emph{ribbon} in a tableau, or a diagram, is a connected strip of
  boxes~$R$ that are totally ordered by their contents. (Recall from
  \autoref{SS:entries} that the content of the box in row~$a$ and
  column~$b$ is $b-a$.) Therefore, a ribbon does not contain a
  \Diagram[scale=0.3,border=false,align=bottom]{2^2}-square, and if
  $(a,b)\in R$ then at most one of $(a+1,b)$ and $(a,b-1)$ belongs
  to~$R$.  The \emph{head} of a ribbon~$R$ is the unique node of maximal
  content.  A \emph{ribbon tableau} is a tableau that is tiled by
  ribbons. A box is a ribbon of length~$1$, so every tableau is a ribbon
  tableau.

  \keyword{\RibbonTableau (x,y) [options] {ribbon specifications}}

  Like the other commands, the $(x,y)$-coordinates are optional and are
  required if, and only if, the diagram is being used as part of a
  \keyword{tikzpicture} environment. All options for the
  \keyword{\Tableau} command can be used for the ribbon command, so we
  refer to \autoref{S:Tableau} for a description of the available
  options.

  % --------------------------------------------------------------
  \subsubsection{Ribbon specifications}
  Unlike the \keyword{\Tableau} command, the entries of a ribbon tableau
  are given by ribbon specifications (rather than tableau)
  specifications. Ribbon specifications are also used by the three keys
  \option{ribbons}, \option{pats}, and \option{snobs}, which were
  introduced in \autoref{SS:TableauOptions}.

  To understand the ribbon specifications, observe that if $(a,b)$ is
  the head of a ribbon, then we can walk along the ribbon by specifying
  whether the \textsf{r}ow index increases or the \textsf{c}olumn index
  decreases. That is, a ribbon is uniquely determined by specifying its
  head $(a,b)$ together with a sequence of $\textsf{r}$'s and
  \textsf{c}'s to indicate when the row index increases, or the column
  index decreases, respectively. For example, vertical and horizontal
  ribbons are given by a sequences of \textsf{r}'s and \textsf{c}'s,
  respectively:

  \begin{example}
  \aTabset{align=top, no border}
  \RibbonTableau{11rrrr} \qquad
  \RibbonTableau{16ccccc}
  \end{example}

  The border of a ribbon tableau is the smallest (skew) partition that
  contains all of its ribbons.  In the last example shows, the
  \option{no border} key is used to disable the ribbon tableau border so
  that we can better see the ribbon, which is the full diagram in these
  two cases.

  The following diagram shows a see-sawing ribbon with head in row~$1$
  and column~10, and tail in row~$5$ and column~$1$.

  \begin{example}
  \RibbonTableau{1{10}crcrcrcrccccc}
  \end{example}

  As with tableau entries, each box in a ribbon can be preceded with a
  style specification, either using \keyword{*} for the \option{star
  style} or using \keyword{[...]} for more customised style
  specifications.

  \begin{example}
  \RibbonTableau{
      *1{10}c*rc*rc*rc*rc*cc*cc,
      *18c[fill=red]rc[fill=blue]rc*rc*cc[fill=teal]c,
      [fill=green]16c*rc*rc*cc,
      *14c[{draw=purple,ultra thick}]cc[fill=orange]r,
      [{fill=yellow,draw=red,ultra thick}]23
  }
  \end{example}

  In particular, the yellow box in this example highlights that boxes
  are ribbons of length~$1$. Most of the time, you want to style the
  entire ribbon rather than styling the individual boxes in the ribbon.
  Optionally, the style for the entire ribbon can be given inside
  parentheses $(...)$ at the \textit{start} of the ribbon. Unlike the
  other style specifications, the $*$-shorthand for the \option{star
  style} cannot be applied to an entire ribbon.

  \begin{example}
  \RibbonTableau{
      (fill=red)1{10}crcrcrcrccc_Ccc,
      (fill=orange)18crcrc*rcc_Bcc,
      (fill=yellow)16crcr[fill=cyan]c_Acc,
      (fill=green)14cccr,
      (fill=blue)23
  }
  \end{example}

  Any styles for a ribbon are applied to the region bounded by  the
  closed path given by the border of the ribbon. The ribbon style is
  applied first, after which any styled boxes in ribbon are drawn.  As
  this example shows, the optional style of any box in the ribbon takes
  precedence over the style of the full ribbon.

  Finally, it is often necessary to label some of the boxes in the
  ribbon. Optionally, text can be added to the boxes in a ribbon by
  supplying it as a \textit{subscript} to the corresponding entry in the
  ribbon specification:

  \begin{example}
  \RibbonTableau[french]    { 12_1 c_2 r_3 } \quad
  \RibbonTableau[ukrainian] { 12_a c_b r_c } \quad
  \RibbonTableau[australian]{ 12_{1_a} c_{2_b} r_{3_c} }
  \end{example}

  Here we have put spaces between the entries for the different boxes
  in the ribbon for clarity. There are often many ways to draw the same
  ribbon tableau, especially if the entries have styling.

  \begin{example}
  \tikzset{Fill/.style={fill=#1!20!white},
    B/.style={Fill=blue}, R/.style={Fill=red}, Y/.style={Fill=yellow}}
  \RibbonTableau{ [B]12_1  [R]c_2   [Y]r_3} \qquad
  \RibbonTableau{ [B]12_1, [R]11_2, [Y]21_3 } \qquad
  \Tableau{       [B]2     [R]1,    [Y]3 }
  \end{example}

  As shown, the easiest way to draw this particular tableau is using the \keyword{\Tableau} command.

  There is no dedicated syntax for putting a label on the boundary
  between two boxes in the diagram, but this can be done using the named
  anchors of~\autoref{E:NodeNames}.

  \begin{example}
  \RibbonTableau[shifted, tikz after={
      \node at (A-1-2.east){$1$};
      \node at (A-2-2.east){$2$};
  }]{ 14c, 12c, 23c }
  \end{example}

  Here is an example of a $3$-ribbon skew tableau.

  \begin{example}
  \RibbonTableau[skew={2^2,1^2},skew border]{
     14c_0r,15r_1c, 18c_7c,26r_9r,
     34c_2c,35r_8r,42r_3c, 44c_4r,
     54r_6c,62c_5r
  }
  \end{example}

  We have now seen the full ribbon specifications. To summarise:
  \begin{itemize}
    \item The ribbon specification starts with optional \TikZ-styling
    for the ribbon, enclosed in $(...)$.
    \item The first entry in the ribbon is given as
    \textsf{a}\textsf{b}, if the head of the ribbon is in row
    \textsf{a} and column \textsf{b}. The remaining entries in the
    ribbon are specified by a sequence of \textsf{r}'s and \textsf{c}'s,
    depending on whether the next box in the ribbon is given by
    increasing the row index, or decreasing the column index,
    respectively.
    \item Optionally, each box in the ribbon, including the head, can be
    given \TikZ-styling by prefixing it with a $*$, which gives the
    ribbon \option{star style}, or by giving \TikZ-styling keys inside
    square brackets $[...]$.
  \end{itemize}

  Finally, when drawing the border, ribbons in a
  \keyword{\RibbonTableau} are assumed to be contained in the smallest
  Young diagram that contains the ribbons. This said, it is up to you to
  ensure that the boxes in the ribbon do not have negative column indices.
  Inside a \keyword{\Diagram} or \keyword{\Tableau} command, any ribbons
  added using \option{ribbons}, or \option{snobs}, do not affect the
  border of the diagram or tableau, and it is your responsibility to
  ensure that the boxes in the ribbon are inside the diagram or tableau.
  This said, it is a useful feature to be able to place boxes outside of
  the diagrams.

  \option[]{ribbons}[comma separated ribbon specifications]
  \option*[]{paths}[comma separated ribbon specifications]
  \option*[]{snobs}[comma separated ribbon specifications]

  You can add \option{ribbons}, \option{paths} and \option{snobs} to a
  \keyword{\RibbonTableau} in exactly the same way that you add them to
  \keyword{\Tableau}. At first sight, it seems unnecessary to add
  \option{ribbons} and \option{snobs} because ribbon tableaux are
  composed of ribbons. The point is that any ribbon added to a tableau
  using \option{ribbons} or \option{snobs} is not assumed to be inside
  the border of the tableau.

  \begin{example}
  \tikzset{A/.style={fill=green!10, text=teal},
           R/.style={fill=yellow!10, text=red}}
  \RibbonTableau[
    ribbons={[A]15_A,[A]24_A,[A]41_A, [R]14_R,[R]33_R}]
    {11, (fill=blue!10)12rc, 14crrcc}
  \end{example}

  \option[draw=\aTableauColour{Inner}, thin]{ribbon style}{\TikZ-styling}
  \option*[-]{ribbon box}{\TikZ-styling}

  Use the \option{ribbon style} and \option{ribbon box} options to
  append to the default styling of the ribbons and the boxes in the
  ribbons, respectively. By default, the full ribbons has an inner wall,
  but the boxes in ribbons have no styling. If you want inner walls,
  then they can be added using the \option{ribbon box} key.

  \begin{example}
  \RibbonTableau[ribbon style={draw=red, thick,
    fill=orange!20}]{16_1r_2c_3c_4c_5c_6r_7c_8}
  \RibbonTableau[ribbon box={fill=orange!20,
    draw=magenta}]{16_1r_2c_3c_4c_5c_6r_7c_8}
  \end{example}

  Ribbons are drawn by first drawing the full ribbon, applying
  \option{ribbon style}, then the empty boxes in the ribbon are drawn,
  and, finally, any boxes in the ribbon that have styling or an entry
  are added. In particular, if the style \option{ribbon box} draws an
  outline around a box then this has precedence over any outline added
  by \option{ribbon style} since \option{ribbon box} is applied last.

  % --------------------------------------------------------------
  \subsection{Multidiagrams and multitableaux}\label{S:Multitableau}
  \indexcmd{Multidiagram}
  \indexcmd{Multitableau}
  \index{diagram!multidiagram}
  \index{tableau!multitableau}

  Multitableaux and multidiagrams are $\ell$-tuples of tableaux and
  diagrams, respectively. These diagrams appear in many places in representation
  theory, such as when considering representations of wreath products
  or cyclotomic Hecke algebras. For convenience, \aTableau provides
  the \keyword{\Multidiagram} and \keyword{\Multitableau} commands for
  drawing these diagrams, even though it is not difficult to construct
  such tableaux and diagrams using the \keyword{\Tableau} and
  \keyword{\Diagram} commands.

  \keyword{\Multidiagram (x,y) [options] {multipartition specifications} }\newline
  \keyword{\Multitableau (x,y) [options] {multitableau specifications}   }

  Our preferred notation for a multipartition $\blam$ is to write
  $\blam=(\lambda^{(1)}|\lambda^{(2)}|\dots|\lambda^{(\ell)})$, where
  $\ell\ge1$ is the \emph{level} and the partitions
  $\lambda^{(1)},\dots,\lambda^{(\ell)}$ are the \emph{components}
  of~$\blam$. Similarly, a multitableau is written as
  $\T=(\T^{(1)}|\dots|\T^{(\ell)})$, where the tableaux
  $\T^{(1)},\dots,\T^{(\ell)}$ are the \emph{components} of~$\T$.
  Accordingly, in the \keyword{\Multidiagram} and
  \keyword{\Multitableau} commands, the pipe symbol \keyword{|} is used
  to separate components:

  \begin{example}
  \aTabset{scale=0.7}
  \Multidiagram{3,2^2|2,1,1|1}
  \Multitableau[box font=\tiny]
      { 123,45,67|89,{{10}},{{11}}|{12}{13}{14} }
\end{example}

  As shown, the \keyword{\Multidiagram} command accepts exponential
  notation for multipartitions. The entries in a \keyword{\Multitableau} can
  be given optional styling specifications, exactly as inside the
  \keyword{\Tableau} command.

  \begin{example}
  \tikzset{R/.style={fill=red!10,text=magenta}}
  \Multitableau{1*24,*68|[R]9{10},{{11}}}
  \end{example}

  Multitableaux and multidiagrams can, in principle, have arbitrary
  level. In practice, the level is constrained by the page width.

  \begin{example}
  \Multitableau[french]{1,2|3,4|5,6|7,8|9,{{10}}}
  \end{example}

  Both the \keyword{\Multitableau} and \keyword{\Multidiagram} commands
  accept a special component, \keyword{...}, that is used to add dots between the
  separators:

  \begin{example}
  \aTabset{scale=0.7}
  \Multidiagram{3,2^2|...|1}
  \Multitableau[box font=\tiny]
      {123,45,67|...|{12}{13}{14}}
  \end{example}

  The \keyword{\Multitableau} and \keyword{\Multidiagram} commands
  accept most of the options of the \keyword{\Tableau} and
  \keyword{\Diagram} commands, together with a few options that are
  specific to multitableaux and multidiagrams. This section describes
  the new options, and highlights how some of the other options are used.

  \option[]{english}
  \option*[]{french}
  \option*[]{ukrainian}
  \option*[english]{australian}

  All four tableaux conventions are supported for multitableaux and
  multidiagrams, with the caveat that all component diagrams use the
  same convention.

  \begin{example}
  \aTabset{scale=0.7}
  \Multidiagram[french]{3,2^2|...|1}
  \Multitableau[ukrainian, box font=\tiny]
      {123,45,67|...|{12}{13}{14}}
  \end{example}

  \option[]{conjugate}
  \index{conjugate!multidiagram}
  \index{conjugate!multitableau}
  \index{multidiagram!conjugate}
  \index{multitableau!conjugate}

  The \option{conjugate} option prints the conjugate mutlitableaux and
  multidiagrams. Conjugation for multitableaux and multidiagrams reverses
  the order of the components and then conjugates the component
  diagrams.

  \begin{example}
  \aTabset{scale=0.6, box font=\scriptsize}
  \Multitableau[conjugate]{ 123,45 | 67,89} \quad
  \Multidiagram[conjugate]{ 3,2 | 1^2 }
  \end{example}

  \option[()]{delimiters}[pair of \LaTeX{} delimiters]
  \option*[(]{left delimiter}[a \LaTeX{} delimiter]
  \option*[)]{right delimiter}[a \LaTeX{} delimiter]

  The delimiter options control the delimiters that are put on the left
  and right of multitableaux and multidiagrams. These options accept any
  \LaTeX{} delimiter.

  \begin{example}
  \aTabset{scale=0.7}
  \Multidiagram[left delimiter=\langle,
      right delimiter={]}]{2,1|1} \quad
  \Multidiagram[delimiters={\|}{\}} ]{1^2|2}
  \end{example}

  To remove a delimiter, set \option{left delimiter} or
  \option{right delimiter} to empty.

  \begin{example}
  \Multitableau[left delimiter=, right delimiter=]
    {123,45,67|{12}{14}}
  \end{example}

  \option[\textbackslash textendash]{empty}[any \LaTeX{}]

  The \option{empty} option determines what is printed when a component
  diagram is empty. By default, the en-dash symbol \textendash{} is
  used.

  \begin{example}
  \Multitableau{ 123,45 | | 67,89} \par\bigskip
  \Multidiagram[empty=$\emptyset$]{ 3,2 | | 2^2 }
  \end{example}

  \option[]{entries}[contents,first,hooks,last,residues]
  \option*[]{charge}[$|$-separated list of charges]
  \index{contents}
  \index{residues}
  \index{contents!multitableau}
  \index{first tableau!multitableau}
  \index{hooks!multitableau}
  \index{last tableau!multitableau}
  \index{residues!multitableau}
  \index{entries!multitableau}
  \index{multidiagram!show}
  \index{multitableau!contents}
  \index{multitableau!first}
  \index{multitableau!hooks}
  \index{multitableau!last}
  \index{multitableau!residue}

  Use the \option{entries} key to draw particular types of tableau of the
  specified shape. Use \option{charge} to provide offsets in each
  component when using \option{entries=contents} and
  \option{entries=residues} (and no charge should be set when using
  \option{entries=first} and \option{entries=last}).

  The possible choices are:
  \begin{itemize}

    \item\option{entries=first} print the \emph{first} \textbf{standard} tableau of this
    shape, which has the numbers $1,2\dots,n$ entered in order from top
    left to right along down successive rows (with appropriate modifications for
    the non-English conventions).

  \begin{example}
  \Multidiagram[entries=first]{3,1^2|2^2,1}
  \end{example}

    \item\option{entries=last} print the \emph{last} \textbf{standard} tableau of this
    shape, which has the numbers $1,2\dots,n$ entered in order from top
    to bottom down successive columns, and right to left along components (with appropriate modifications for
    the non-English conventions).

  \begin{example}
  \Multidiagram[entries=last]{3,2,2|2^2}
  \end{example}

    \item\option{entries=hooks} print the diagram where each box in each
    component is labelled by the corresponding \emph{hook length}.

  \begin{example}
  \Multidiagram[entries=hooks]{3,1^2|3^3}
  \end{example}

    \item\option{entries=contents} print the diagram where each box is
    labelled by its \emph{content}, which is the row index minus the
    column index.

  \begin{example}
  \Multidiagram[entries=contents,
    charge={0,2}] {3,2,1|2^2}
  \end{example}

    As shown, the \option{charge} offsets the contents in each
    component.

    \item\option{entries=residues} print the diagram where each box is
    labelled by its \emph{residue}, which is the row index minus the
    column index modulo some integer~$e$, which must also be supplied.

    \index{residue}
    \index{tableau!residues}
  \begin{example}
  \Multidiagram[entries=residues, e=2]{3,2,1|1^3}
  \end{example}

  Specifying the \option{charge} offsets the residues in each component.

  \begin{example}
    \Multidiagram[french,entries=residues, e=3,
      charge={1,2}]{3,2,1|1^2}
  \end{example}

  \medskip
  As in \autoref{SS:entries}, residues for the other affine Cartan types
  can be specified using \option{cartan=??}.

  \end{itemize}

  \option[]{label}[a $|$-separated list of labels]

  Use the \option{label} key to add labels to the component diagrams.

  \begin{example}
    \Multitableau[label={1|2}]{123,45,67|{12}{14}}
  \end{example}

  No extra space is allowed for the labels, so use \option{xoffsets}
  and \option{yoffsets} to adjust for wide labels.

  \option[B]{name}[character]

  The \option{name} option is used to change the default prefix for the
  box node names. In a tableau, or diagram, the box names depend on the
  \emph{row} and \emph{column} indices. In a multitableau, or
  multidiagram, the box names depend on the \emph{component}, \emph{row}
  and \emph{column} indices. Explicitly, by default, in multitableaux
  and multidiagrams the names of the take the form \textsf{A-k-r-c},
  where~\textsf{k} is the component index,~\textsf{r} is the row index,
  and~\textsf{c} is the column index of the box. The \textsf{B} can be
  changed like using the \option{name} key.

  \begin{example}
  \Multitableau[name=A, tikz after = {
    \draw[red, thick,<->](A-1-2-2.south east) to
         [out=315,in=225] (A-2-2-1.south west);
    }] { 123,4*5 | 67,*89}
  \end{example}

  \option[]{ribbons}[a $|$-separated list of ribbon specifications]
  \option*[]{paths}[a $|$-separated list of ribbon path specifications]
  \option*[]{snobs}[a $|$-separated list of ribbon specifications]

  The \option{ribbons}, \option{path}, and \option{snobs} keys work in exactly the
  same way for multitableaux and multidiagrams as they do for tableaux
  and diagrams except that the ribbons for different components are
  separated by a pipe $|$.

  \begin{example}
  \tikzset{R/.style={fill=red!10, opacity=0.5},
           Y/.style={fill=yellow!20, opacity=0.5}}
  \Multitableau[ribbons={(R)11*r|(Y)12rc}]
      { 123,45 | 67,89}
  \end{example}

  Notice that the $4$ is the first component has disappeared because
  the second node in the ribbon \textsf{(R)11*r} has $*$-styling, which
  writes over the $4$. (One way to recover the missing entry is to use the
  ribbon specification \textsf{(R)11*r\textunderscore4}.)

  \option[]{rows}[a decimal number]

  The \option{rows} option sets the number of rows covered by the
  delimiters in multitableaux and multidiagram.  By default, the
  \keyword{\Multitableau} and \keyword{\Multidiagram} commands choose
  the size of the delimiters to match the component diagrams, which may
  not be what you want especially when using the \option{australia} and
  \option{ukrainian} conventions. The value of \option{rows} can be a
  decimal number.

  \begin{example}
  \Multidiagram[ukrainian,scale=0.5]{3,2^2|...|2,1^2}
  \end{example}

  \begin{example}
  \Multitableau[rows=3,scale=0.8,box font=\tiny]
       {{1_1}{1_1}{1_1}{2_1},{2_1}{2_1}{2_1} |
        {1_2}{3_3},{{2_2}} |
        {1_3}{1_3},{{2_3}}}
  \end{example}

  \begin{example}
  \Multitableau[ukrainian,rows=2.5,scale=0.8,box font=\tiny]
       {{1_1}{1_1}{1_1}{2_1},{2_1}{2_1}{2_1} |
        {1_2}{3_3},{{2_2}} |
        {1_3}{1_3},{{2_3}}}
  \end{example}

  \option[true]{separators}[true/false]
  \option*[false]{no separators}[false/true]

  When \option{separators} is true, delimiters are drawn around the
  component diagrams in a multitableaux and a multidiagram and
  separators are drawn between the component shapes, and
  \option{no separators} is the inverse option. By default, separators
  and delimiters are drawn.

  \begin{example}
  \Multidiagram[no separators,scale=0.5]
    {3,2^2|2,1^2} \par\bigskip
  \Multitableau[separators,scale=0.8]
    {123,45,67 | 89,{10}{11}}
  \end{example}

  \option[$|$]{separator}[character]

  The \option{separator} determines what is printed between the
  component diagrams in multitableaux and multipartition. By default,
  \option{separator=|} draws a straight line between the
  components, but any character can be used.

  \begin{example}
  \Multitableau[separator={,}]{ 123,45 | 67,89} \par\bigskip
  \Multidiagram[separator=:]{ 3,2 | 2^2 }
  \end{example}

  \option[\aTableauColour{Main}]{separator colour}[\LaTeX{} colour]

  The \option{separator colour} sets the colour of the delimiters and
  the separator between component diagrams. By default, the separators
  are the same colour as the diagram border.

  \begin{example}
  \Multitableau[separator colour=red]{123,45 | 67,89} \par\bigskip
  \Multidiagram[separator color=brown, separator=:]
    {3,2 | 2^2 }
  \end{example}

  \option[0.3]{separation}[a decimal number (the distance in \unit{cm})]

  The \option{separation} key sets the distance between the separators
  and the component tableaux and diagrams.

  \begin{example}
  \Multitableau[separation=0.1]{123,45 | 67,89} \par\bigskip
  \Multidiagram[separation=0.8]{3,2 | 2^2}
  \end{example}

  \option[]{skew}{a $|$-separated list of partitions}

  Skew multishapes can be drawn using the \option{skew} option to
  specify a $|$-separated list of inner shapes.

  \begin{example}
    \Multitableau[skew={2,1|1}]{ 123,45 | 7{10},89} \par\bigskip
    \Multidiagram[skew={1|2,1}, skew boxes]{ 3,2 | 2^2 }
  \end{example}

  There is no command for drawing shifted multitableau or multidiagrams,
  however, such diagrams can be be drawn using an appropriate
  \option{skew} key.  In the same way, it is possible to draw
  multitableaux and multidiagrams with components that are a mixture of
  non-skew, skew and shifted shapes.

  \begin{example}
    \Multitableau[skew={0,1|0,1}]{ 1236,45 | 7{10}{11},89} \par\bigskip
    \Multidiagram[skew={|0,1}]{ 3,2 | 2,1 }
  \end{example}

  \option[]{tabloid}

  Use the \option{tabloid} key for multitabloid diagrams and tableaux.

  \begin{example}
    \Multitableau[tabloid]{ 123,45 | 67,89} \par\bigskip
    \Multidiagram[tabloid]{ 4,2 | 2^2 }
  \end{example}

  \option[0]{xoffsets}[comma separated list of $x$-offsets]
  \option*[0]{yoffsets}[comma separated list of $y$-offsets]

  The \keyword{\Multitableau} and \keyword{\Multidiagram} commands try
  to draw the diagrams as compactly as possible with their first rows
  aligned, and the distance between the separators given by the value of
  \option{separation}. Use the \option{xoffsets} to offset the
  $x$-coordinates of the component diagrams and \option{yoffsets} to
  offset their $y$-coordinates.

  \begin{example}
    \Multitableau[xoffsets={0.5,0.2}]{ 123,45 | 67,89} \par\bigskip
    \Multidiagram[yoffsets={0,1.5}]{ 4,2 | 2^2 }
  \end{example}

  When using \option{xoffsets} or \option{yoffsets}, you may want to use
  \option{no separators} to disable the separators between component
  shapes. For example, here is a homogeneous Garnir tableau~
  \cite{KMR:UniversalSpecht}.

  \begin{example}
    \Multidiagram[entries=first, no separators,
      xoffsets={0|-1.1}, yoffsets={0|-1},
      styles={O={fill=orange!50}, P={fill=purple!50}},
      ribbon style={draw=red,double,thick,fill=white},
      snobs={|(O)24_{15}c_{14}, (P)26_{17}c_{16}, 27_{18},
        31_{11},  (P)33_{13}c_{12}}]{1|7^2,4,1}
  \end{example}

  % --------------------------------------------------------------
  \section{Abacuses} \label{S:Abacus} \index{abacus} \indexcmd{Abacus}

  Gordon James introduced the abacus, with beads and runners, as another
  way to represent a partition~\cite{James:YoungD}. The abacus is
  particularly useful in modular representation theory, where the number
  of runners is the (quantum) characteristic. Abacus combinatorics are
  now used to help many algebras beyond their initial appearance in the
  representation theory of the symmetric groups.

  The partition corresponding to an abacus is given by counting the
  number of empty bead positions before each bead on the abacus. The
  \keyword{\Abacus} command, which draws an abacus representation of a
  partition, has a similar syntax to the tableau and diagram commands.

  \keyword{\Abacus (x,y) [options] {number of runners} {bead specifications}}

  As with other \aTableau commands, the $(x,y)$-coordinates are
  necessary if, and only if, the abacus is part of a
  \keyword{tikzpicture} environment.  The number of runners is a
  positive integer that specifies the number of abacus runners.

  % --------------------------------------------------------------
  \subsection{Bead specifications}

  In their simplest form, the bead specifications are a comma separated
  list of non-negative integers specifying a partition. Partitions can
  be given either as comma separated lists of non-negative integers, or
  using exponential notation. The full bead specifications add optional
  styling and bead labels.

  Here are some examples showing basic usage of the \keyword{\Abacus}
  command:

  \begin{Example}
  \aTabset{align=top}
  \Abacus{1}{2,1,1}     \qquad \Abacus{2}{2,1^2,0^3} \qquad \Abacus{3}{2,1^2,0^5} \qquad
  \Abacus{4}{2,1^2,0^5} \qquad \Abacus{5}{2,1^2,0^5} \qquad \Abacus{6}{2,1^2,0^5}
  \end{Example}

  The beads in an abacus correspond to the parts of the partition. Just
  as with the \keyword{\Tableau} command, each of the beads can be given
  optional styling, which can either be given by prepending a
  \keyword{*}, which applies the \option{abacus star style}, or by
  giving \TikZ styling-keys inside square brackets \keyword{[...]}.
  When exponential notation is used, the styles are applied to all of the
  associated beads.

  \begin{example}
  \aTabset{align=top}
  \Abacus{3}{3,*2^3,1}  \qquad
  \Abacus{4}{2,*1,[ball color=red]1^2, *1,
    [ball color=orange]1,[ball color=brown]0}
  \end{example}

  In particular, in the right-hand abacus, the two beads corresponding
  to \keyword{1^2} are coloured red, whereas the other three beads that
  correspond to a~$1$ are either orange or an off-white colour, which is
  the colour given by the \option{abacus star style}. As with the
  tableaux commands, more complicated bead styles can be defined using
  \keyword{\tikzset}.

  In addition, to applying style to the individual beads on the abacus,
  labels for the beads can (optionally) be given as subscripts in the
  bead specifications. Again, the same labels are applied to all of the
  corresponding beads when exponential notation is used.

  \begin{example}
  \aTabset{align=top}
  \tikzset{R/.style={ball color=red, text=yellow}}
  \Abacus{3}{5_5, 4_4, 3_3, 2_2,0_0} \quad
  \Abacus{4}{*5^2_5, [R]4^3_4, 3, 2_2,*0^2_{oo}} \quad
  \Abacus{5}{8^2_-,7_+,5_a,4^2_b,1_c^3,1_d}
  \end{example}

  The bead labels are arbitrary, however, anything wider than the bead
  will spill into the abacus. Traditionally, the beads are unlabelled,
  but your can give optional labels to as many beads as you like.

  % --------------------------------------------------------------
  \subsection{Abacus keys}

  The abacus keys, or options, control the general appearance of the
  abacuses drawn by the \keyword{\Abacus} command. Many of the options, or keys, for
  tableaux and diagrams can also be applied to abacuses, including
  \option{align},
  \option{name},
  \option{scale},
  \option{tikz after},
  \option{tikz before}, and
  \option{tikzpicture}. See \autoref{S:keys} for the complete list.

  \option[true]{south}{true/false}
  \option*[false]{north}{false/true}
  \option*[false]{east}{false/true}
  \option*[false]{west}{false/true}

  Just like tableaux, abacus have four different conventions.  By
  default, abacuses are drawn in the southerly direction, from top to
  bottom. Using these keys, abacuses can also be drawn to the north,
  east and west.

  \begin{example}
    \Abacus[south]{2}{4^3,2,1} \qquad % the default
    \Abacus[east]{2}{4^3,2,1}  \par\smallskip\par
    \Abacus[north]{2}{4^3,2,1} \qquad
    \Abacus[west]{2}{4^3,2,1}
  \end{example}

  \option[-\,-\,]{abacus top}[-\,-\,-,...,none]
  \option*[none]{abacus bottom}[-\,-\,-,...,none]

  \begin{Example}
  \aTabset{align=top}
  \Abacus[abacus top=---,  abacus bottom=none]{3}{2,1^2,0^3} \quad % the default
  \Abacus[abacus top=---,  abacus bottom=---]{3}{2,1^2,0^3}  \quad
  \Abacus[abacus top=---,  abacus bottom=...]{3}{2,1^2,0^3}  \quad
  \Abacus[abacus top=...,  abacus bottom=none]{3}{2,1^2,0^3} \quad % the default
  \Abacus[abacus top=...,  abacus bottom=---]{3}{2,1^2,0^3}  \quad
  \Abacus[abacus top=...,  abacus bottom=...]{3}{2,1^2,0^3}  \quad
  \Abacus[abacus top=none, abacus bottom=none]{3}{2,1^2,0^3} \quad % the default
  \Abacus[abacus top=none, abacus bottom=---]{3}{2,1^2,0^3}  \quad
  \Abacus[abacus top=none, abacus bottom=...]{3}{2,1^2,0^3}  \quad
  \end{Example}

  \option[text=\aTableauColour{Main},text=\aTableauColour{StarStyle}]{abacus star style}
     [\TikZ-style keys]

  The \option{abacus star style} key appends \TikZ-style keys to the
  $*$-style for beads.

  \begin{example}
  \Abacus{3}{5,4,*1^2,0^4} \qquad
  \Abacus[abacus star style={ball color=yellow}]
    {3}{5,4,*1^2,0^4}
  \end{example}


  \option[]{runner}

  \option[]{bead height}

  \option[]{bead width}

  \option[\aTableauColour{Main}]{bead}[]

  The \option{bead} key sets  the bead colour.

  \begin{example}
    \Abacus{2}{2^3,1} \qquad
    \Abacus[bead=black]{3}{4^3,2,1} \qquad
    \Abacus[bead=red]{4}{4^3,[ball color=blue]2,1}
  \end{example}

  The \option{bead} key changes the colour of every bead on the
  abacus. As shown, use the \TikZ-style \keyword{ball colour} to
  change the colour of individual beads.

    \option[\scriptsize]{bead font}[]

    \option[0.3]{bead size}[bead diameter in \unit{cm}]

    \option[0.35]{bead sep}[]

    \option[white]{bead text}[]

    \option[false]{beta numbers}[false/true]

    When \option{beta numbers} is true, the numbers in the bead
    specifications should be entered as \emph{beta numbers}. The beta
    numbers give the bead positions, which are numbered $0,1,\dots$,
    starting from the first row and then continuing in this way in
    subsequent rows. Up to shift, bead numbers are first column hook
    lengths. In particular, beta numbers are pairwise distinct.

  \begin{example}
    \Abacus{3}{3,2^2} \quad
    \Abacus[beta numbers]{3}{5,3,2} \quad
    \Abacus[beta numbers]{3}{5,4,3,0}
  \end{example}

  There is no inverse key to \option{beta numbers}, however,
  \option{beta numbers=false}
    \option[\aTableauColour{Inner}]{runner}[]

    \option[0.35]{runner sep}[]

    \option[\aTableauColour{Inner}]{tick}[]

    \option[0.1]{tick width}[]

  \begin{example}
  \Abacus{3}{5,4,1,1}
  \Abacus[entries=shape,bead text=yellow]{3}{5,4,1,1}
  \Abacus[entries=beta,bead text=red]{3}{5,4,1,1}
  \Abacus[entries=rows]{3}{5,4,1,1}
  \Abacus[entries=residue]{3}{5,4,1,1}
  \end{example}

  \begin{example}
    \tikzset{B/.style={ball color=LightSkyBlue}}
    \Abacus[beta numbers]{4}{6,4,3,1,0}
    \quad $\longrightarrow$\quad
    \Abacus[beta numbers]{4}{7,5,4,2,1,[B]0}
  \end{example}

  % --------------------------------------------------------------
  \section{Examples from the literature}

  This section shows how to draw some tableaux that appear
  in the literature. All of these diagrams predate this package. The
  aim of this section is not to showcase uses of this package but,
  rather, to show how some preexisting diagrams could have been drawn.

  Diagrams like the following are common. Note that the use of a ribbon
  to add the $\alpha$ in row~$6$ and column~$8$.

  \begin{example}
  \Diagram[french, no boxes,
    ribbons={*68_\alpha},
  ] {15,13,12,9,8^2,5,3}
  \end{example}

  I do not remember where I found the first example:

  \begin{example}[lefthand width=0.24\textwidth]
  \tikzset{L/.style={red,->}, R/.style={red,<-}}
  \RibbonTableau[skew={4,3,2,1},scale=0.8,
    paths = { (L)15c, (L)17c, (L)24c, (L)26c,
      (R)32r,(R)41r,(R)52r,(R)61r, (R)34c
    },
    tikz after = { % node labels: row/col/label
      \foreach \r/\c/\l in {1/6/0, 1/8/6, 2/5/3, 2/7/8}
        { \node at (A-\r-\c.west){\l};}
      \foreach \r/\c/\l in {5/1/1, 4/2/2, 3/3/5, 7/1/4, 6/2/7}
        { \node at (A-\r-\c.south){\l};}
    }
  ]{
      16c,18c, 25c, 27c, 33r, 42r, 51r, 62r,71r
  }
  \end{example}

  Mendes~ \cite{Mendes:hooks} uses these tableau to give a proof of the
  Murnaghan-Nakayama rule.

  \begin{example}
    \tikzset{C/.style={circle,draw=blue, minimum size=3.5mm,
      fill=white,thick}}
    \Diagram[paths={
      [C]13_1cc_\bullet, [C]21_2r_\bullet,
      [C]23_3c_\bullet, [C]14_4
    }]{4,3,1} \qquad
    \Diagram[ribbon style={rounded corners}, paths={
      [C]12_1cr_\bullet, [C]14_2c_\bullet,
      [C]23_3c_\bullet, [C]31_4
    }]{4,3,1} \quad

  \end{example}

  The following tableau comes from Fayers
  paper~\cite{Fayers:DyckTilings}, which is uses Dyck tilings to
  understand homogeneous Garnir relations for KLR algenras of type~$A$.

  \begin{example}
  \RibbonTableau[skew={1^2}, ukrainian, scale=0.7,
    ribbons={(draw=none)21_m}
  ]{
     12,16c_\circ c_\circ c_\circ r_\circ r_\circ *r,
     18crcccrr*r,19,1{10},1{11},1{12},
     22,29crcccrr*rccrcrr,
     2{12}ccrcrcccrr*r_lccrcrrr,
     31,*32,41,42,51,52,53,
     62cr,81,91,{10}1,{10}2,{11}1,{11}2
  }
  \end{example}




  \begin{example}[lefthand width=0.3\textwidth]
  \newcommand\Sym[2]{\begin{array}{l}#1\\#2\end{array}}
   \Tableau[ukrainian, box font=\scriptsize,
      tikz after = {\draw[ultra thick,teal](A-2-3.east)--(A-2-2.south)
                          --(A-3-2.west)--(A-3-3.north)--cycle;
   }]{
      {\Sym11}{\Sym11}{\Sym11}{\Sym0s},
      {\Sym11}{\Sym11}{\Sym11}{\Sym0s},
      {\Sym11}{\Sym11}{\Sym{s^*}s}{\Sym0f},
      {\Sym11}{\Sym11}{\Sym11},
      {\Sym11}{\Sym11}
  }
  \end{example}

  The last example, also from
  \cite{bowman2023quiverpresentationsisomorphismshecke}, is a little
  more involved. Most of the diagram is drawn using \textit{pics} from
  \TikZ. From the perspective of this manual, the most interesting
  feature is that it gives a non-trivial example of how to use the named
  nodes for the tableaux boxes; see \autoref{E:NodeNames}.

\begin{Example}[label=Ex:waves]
\begin{tikzpicture}[
   Cap/.style={out=45, in=135}, % caps are drawn with to[Cap]
   Cup/.style={out=315,in=225}, % cups are drawn with to[Cup]
   every node/.style={font=\scriptsize},
   redribbon/.style={fill=red!40,opacity=0.4},
   % define pics for drawing the curvy up and down strings
   pics/ustring/.style n args = {4}{% {colour}{first coord}{wave coords}{last coord}
      code = {
          \def\last{#2} % should not be necessary
          \draw[thick,#1](T-|#2.north west)node[above=-0.155]{$\vee$}--(#2.north west)
              foreach [remember=\pt as \last (initially #2)] \pt in {#3}
                  {to[Cup](\last.north east) to[Cap] (\pt.north west)}
              to[Cup] (#4.north east) -- (#4.north east|-T)node[above=-0.27]{$\wedge$};
      }
   },
   pics/dstring/.style n args = {4}{% {colour}{first coord}{wave coords}{last coord}
      code = {
          \def\last{#2} % should not be necessary
          \draw[thick,#1](O-|#2.south west)node[below=-0.13]{$\wedge$}--(#2.south west)
              foreach [remember=\pt as \last (initially #2)] \pt in {#3}
                  {to[Cap](\last.south east) to[Cup] (\pt.south west)}
              to[Cap] (#4.south east) -- (#4.south east|-O)node[above=-0.13]{$\vee$};
      }
   },
 ]
 \coordinate (O) at (0,0); \coordinate (T) at (0,3.2);
 \draw(-2,0)--(2.5,0) (-2,3.2)--(2.5,3.2);
 \Diagram(0,0)[ukrainian, inner style=dotted,
    ribbons={(redribbon)24rcrcrc}]{5,4^3,3}
 \pic at (T) {ustring={gray}{A-1-5}{}{A-1-5}};  % up strings
 \pic at (T) {ustring={gray}{A-4-4}{}{A-4-4}};
 \pic at (T) {ustring={gray}{A-5-2}{A-4-3,A-3-4}{A-3-4}};
 \pic at (T) {ustring={gray}{A-5-3}{}{A-5-3}};
 \pic at (T) {ustring={ForestGreen}{A-5-1}{A-4-2,A-3-3,A-2-4}{A-2-4}};
 \pic at (O) {dstring={gray}{A-1-1}{}{A-1-1}};  % down strings
 \pic at (O) {dstring={gray}{A-2-1}{A-1-2}{A-1-2}};
 \pic at (O) {dstring={gray}{A-3-1}{A-2-2,A-1-3}{A-1-3}};
 \pic at (O) {dstring={gray}{A-4-1}{A-3-2,A-2-3,A-1-4}{A-1-4}};
 \pic at (O) {dstring={gray}{A-5-1}{A-4-2,A-3-3,A-2-4,A-1-5}{A-1-5}};
\end{tikzpicture}
\end{Example}

  % --------------------------------------------------------------
  \section{\aTableau commands and options}\label{S:keys}
  \rowcolors{2}{aTableauSkewFill}{}

  The \aTableau package provides the following commands:

  \begin{center}
    \begin{tabular}{Lll}\toprule
      \multicolumn1l{\large\sffamily\color{MidnightBlue}Command}
                     & \large\sffamily\color{MidnightBlue} Diagram
                     & \large\sffamily\color{MidnightBlue} Section \\\midrule
      Abacus         & An abacus for a partition         & \autoref{S:Abacus}\\
      Diagram        & A Young diagram for a partition   & \autoref{S:Diagram}\\
      Multidiagram   & An $\ell$-tuple of Young diagrams & \autoref{S:Multitableau} \\
      Multitableau   & An  $\ell$-tuple of tableaux      & \autoref{S:Multitableau} \\
      RibbonTableau  & A ribbon tableau                  & \autoref{S:RibbonTableaux} \\
      ShiftedDiagram & A shifted Young diagram           & \autoref{S:Shifted} \\
      ShiftedTableau & A shifted tableau                 & \autoref{S:Shifted} \\
      SkewDiagram    & A skew Young diagram              & \autoref{S:Skew} \\
      SkewTableau    & A skew tableau                    & \autoref{S:Skew} \\
      Tableau        & A tableau                         & \autoref{S:Tableau} \\
      Tabloid        & A tabloid                         & \autoref{S:Tabloid} \\
      \bottomrule
    \end{tabular}
  \end{center}

  In addition, the \keyword{\aTabset} command can be used to set default
  \aTableau options.

  For easier reference, here is the list of \aTableau keys, together
  with a quick explanation of what they do. The last two columns
  indicate whether the options apply to tableau (and diagrams), or to
  abacuses --- or both! Although not listed, American spelling
  variations of all keys are tolerated.

  \begin{xltabular}{\textwidth}{lXcc}
    \toprule
    Key & Meaning & Tableau & Abacus \\
    \midrule
    \endhead
    \option{abacus star style} & Set \TikZ-style of abacus $*$-nodes               & \No  & \Yes\\
    \option{align}             & Set baseline alignment of \aTableau diagram       & \Yes & \Yes\\
    \option{australian}        & Use the Australian convention for tableau         & \Yes & \No \\
    \option{bead height}       & Set row height between beads                      & \No  & \Yes \\
    \option{bead width}        & Set column height between beads                   & \No  & \Yes \\
    \option{bead}              &                                                   & \No  & \Yes \\
    \option{bead font}         &                                                   & \No  & \Yes \\
    \option{bead sep}          &                                                   & \No  & \Yes \\
    \option{bead size}         &                                                   & \No  & \Yes \\
    \option{bead text}         &                                                   & \No  & \Yes \\
    \option{beta~numbers}      &                                                   & \No  & \Yes \\
    \option{border colour}     & Set tableau border colour                         & \Yes & \No \\
    \option{border style}      & Set tableau border style                          & \Yes & \No \\
    \option*{border}           & Draw the tableau border                           & \Yes & \No \\
    \option{box fill}          & Set tableau box fill colour                       & \Yes & \No \\
    \option{box font}          & Set tableau box font                              & \Yes & \No \\
    \option{box height}        & Set tableau box height                            & \Yes & \No \\
    \option{box text}          & Set tableau box text colour                       & \Yes & \No \\
    \option{box width}         & Set tableau box width                             & \Yes & \No \\
    \option*{boxes}            & Draw inner walls around boxes                     & \Yes & \No \\
    \option{cartan}            & Set Cartan type for residues                      & \Yes & \No \\
    \option{charge}            & Set charge for contents and residues              & \Yes & \Yes \\
    \option{conjugate}         & Draw the conjugate tableau/diagram                & \Yes & \No \\
    \option{delimiters}        & Set delimiters for multitableau and multidiagrams & \Yes & \No \\
    \option{dotted cols}       & Specify diagram columns to replace with dots      & \Yes & \No \\
    \option{dotted columns}    & Specify diagram columns to replace with dots      & \Yes & \No \\
    \option{dotted rows}       & Specify diagram rows to replace with dots         & \Yes & \No \\
    \option{east}              & Abacus grows in the easterly direction            & \Yes & \No \\
    \option{empty}             & Symbol for empty tableau in multitableau          & \Yes & \No \\
    \option{english}           & Use the English convention for tableau            & \Yes & \No \\
    \option{entries}           & Draw contents/residues/hooks/first/last tableau   & \Yes & \No \\
    \option{e}                 & Set the quantum characteristic for residues       & \Yes & \Yes \\
    \option{french}            & Use the French convention for tableau             & \Yes & \No \\
    \option{halign}            & Horizontal alignment of box entries and bead labels & \Yes & \Yes \\
    \option{inner colour}      & Set colour of inner tableau wall                  & \Yes & \No \\
    \option{inner style}       & Set style of inner tableau wall                   & \Yes & \No \\
    \option{label style}       & Set style of tableau labels                       & \Yes & \No \\
    \option{label}             & Set tableau label                                 & \Yes & \No \\
    \option{left delimiter}    & Set left delimiter for multitableau               & \Yes & \No \\
    \option{math boxes}        & Typeset box entries in math-mode (true by default)& \Yes & \No \\
    \option{name}              & Prefix of named nodes                             & \Yes & \Yes \\
    \option{north}             & Abacus grows in the northerly direction           & \Yes & \No \\
    \option{ribbon box}        & Define a node for every box on a ribbon path      & \Yes & \No \\
    \option{paths}             & Add paths to a diagram or tableau                 & \Yes & \No \\
    \option{ribbon box}        & Set style of boxes in ribbons                     & \Yes & \No \\
    \option{ribbon style}      & Set ribbon style                                  & \Yes & \No \\
    \option{ribbons}           & Comma separated list of ribbons to add to tableau & \Yes & \No \\
    \option{right delimiter}   & Set left delimiter for multitableau               & \Yes & \No \\
    \option{rows}              & Set number of rows in multitableau or abacus      & \Yes & \Yes \\
    \option{runner}            & Set the colour of the abacus runners              & \No  & \Yes \\
    \option{runner~sep}        & Set distance between abacus runners               & \No  & \Yes \\
    \option{scale}             & Sets the \aTableau scale                          & \Yes & \Yes \\
    \option{separation}        & Set distance between component tableau in multitableau & \Yes & \No \\
    \option{separator colour}  & Set separator colour in multitable                & \Yes & \No \\
    \option*{separators}       & Enable separators in multitableau                 & \Yes & \No \\
    \option{separator}         & Set separator colour in multitableau              & \Yes & \No \\
    \option{shifted}           & Set true for a shifted tableau                    & \Yes & \No \\
    \option{skew border style} & Set \TikZ-style of the skew border                & \Yes & \No \\
    \option*{skew border}      & Set skew border colour                            & \Yes & \No \\
    \option{skew box style}    & Set \TikZ-style of the skew boxes                 & \Yes & \No \\
    \option*{skew boxes}       & Enable drawing of skew boxes                      & \Yes & \No \\
    \option{skew}              & Set inner skew shape                              & \Yes & \No \\
    \option{snobs}             & Comma separated list of snobs to add to tableau   & \Yes & \No \\
    \option{south}             & Abacus grows in the southerly direction           & \Yes & \No \\
    \option{star style}        & Set \TikZ-style of tableau $*$-nodes              & \Yes & \No \\
    \option{styles}            & Short-hand for setting single use \TikZ-styles    & \Yes & \Yes \\
    \option{tabloid}           & Set true for a shifted tableau                    & \Yes & \No \\
    \option{text boxes}        & labels typeset in text-mode (false by default)    & \Yes & \Yes \\
    \option{tick}              & Set the colour of the abacus runner ticks         & \No  & \Yes \\
    \option{tick~width}        & Set the width of the abacus runners               & \No  & \Yes \\
    \option{tikz after}        & \TikZ-code injected after abacus                  & \Yes & \Yes \\
    \option{tikz before}       & \TikZ-code injected before abacus                 & \Yes & \Yes \\
    \option{tikzpicture}       & Add tikzpicture environment keys                  & \Yes & \No \\
    \option{ukrainian}         & Use the Ukrainian convention for tableau          & \Yes & \No \\
    \option{valign}            & Set vertical alignment of box entries and bead labels & \Yes & \Yes \\
    \option{west}              & Abacus grows in the westerly direction            & \Yes & \No \\
    \option{xoffsets}          & Set the $x$-offsets for component diagrams in a multitableau & \Yes & \No \\
    \option{xscale}            & Set the \aTableau $x$-scale                       & \Yes & \Yes \\
    \option{yoffsets}          & Set the $y$-offsets for component diagrams in a multitableau & \Yes & \No \\
    \option{yscale}            & Set the \aTableau $y$-scale                       & \Yes & \Yes \\
    \bottomrule
  \end{xltabular}

  % --------------------------------------------------------------
  \subsection{\aTableau Colours}\label{S:Colours}

  The \aTableau package defines and uses the following colours:

  \begin{center}
    \begin{tabular}{lll}\toprule
       \textcolor{aTableauMain}{Colour}& \textcolor{aTableauMain}{Name}& \textcolor{aTableauMain}{HTML}\\
       \midrule
       \aTableauColour{Inner}     & aTableauInner     & 0073E6 \\
       \aTableauColour{Main}      & aTableauMain      & 00008B \\
       \aTableauColour{SkewFill}  & aTableauSkewFill  & F8F8F8 \\
       \aTableauColour{Skew}      & aTableauSkew      & 818589 \\
       \aTableauColour{StarStyle} & aTableauStarStyle & E6F7FF \\
       \bottomrule
    \end{tabular}
  \end{center}

  All of these colours are defined as HTML colours using the
  \keyword{\definecolor} command provided by \ctan{xcolor}.

  It is possible to change the colours used in the diagrams created by
  \aTableau by changing these colours. However, we recommend using the
  key-value interface instead. It is sometimes useful to be able to use
  these colour names directly in your own styles.

  % --------------------------------------------------------------
  \section{Feature requests and bug reports}

  Please make any feature requests and bug reports on the package github
  page
  \begin{center}
    \href{https://github.com/AndrewMathas/aTableau/}{github.com/AndrewMathas/aTableau/}.
  \end{center}
  Please give as much detail as possible when making such requests.

  Bug reports must be a accompanied by a \textit{minimal working
  example}, which is the smallest possible amount of \LaTeX\ code that
  compiles and demonstrates the problem. This is necessary because if I
  cannot reproduce your problem, then it is unlikely that I will be
  able to fix it.


% ----------------------------------------------------------------------
% indices and bibliography
\bibliography{papers}
\bibliographystyle{andrew}
\printindex

\end{document}
